---
title: "Syntactic Boostrapping MA"
subtitle: "Data V2"
author: "Anjie Cao and Molly Lewis"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc_float: yes
    code_folding: hide 
    number_sections: no
    toc: yes
---


```{r setup, include = F}
library(glue)
library(tidyverse)
library(googlesheets4)
library(metafor)
library(knitr)
library(gridExtra)
library(here)
library(dict)
library(heatmaply)
library(MuMIn)
library(glmulti)
GOOGLE_SHEET_ID <- "1kSL5lpmHcaw9lOp2dhJ_RH15REFe7oZVwMO1vJc930o"
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.height=6, fig.path='Figs/',
                     warning=FALSE, message=FALSE)
theme_set(theme_classic()) # sets global plot theme
```

```{r}
DATA_PATH <- here("data/processed/syntactic_bootstrapping_tidy_data.csv") # make all variables (i.e. things that might change) as capital letters at the top of the scripts

ma_data <- read_csv(DATA_PATH) 
ma_data
```



# Data Overview

```{r}
n_effect_sizes <- ma_data %>%
  filter(!is.na(d_calc)) %>%
  nrow()

n_papers <- ma_data %>%
  distinct(unique_id) %>%
  nrow()

```

There are `r n_effect_sizes` effect sizes collected from `r n_papers` different papers.

Here are the papers in this analysis:
```{r}
ma_data %>%
  count(short_cite) %>%
  arrange(-n) %>%
  DT::datatable()
```
# Forest plot 
```{r}
ma_model <- rma(ma_data$d_calc, ma_data$d_var_calc)
ma_model
forest(ma_model,
       header = T,
       slab = ma_data$unique_id,
       col = "red",
       cex = .7)

```
#funnel plot {.tabset}
## vanilla 
```{r}

ma_data %>% 
  mutate(color = ifelse(sentence_structure == "transitive", "red", "blue"),
         color_sample_size = ifelse(n_1 < 10, "red", ifelse(n_1 < 20, "orange", "yellow")),
         color_confidence = ifelse(inclusion_certainty == 1, "red", "black"))-> ma_data_funnel


ma_data_funnel %>% filter (abs(d_calc) < 5) -> ma_data_funnel_no_outlier

ss_colors <- ma_data_funnel$color
ss_colors_no_outlier <- ma_data_funnel_no_outlier$color 

ma_model_funnel <- rma(ma_data_funnel$d_calc, ma_data_funnel$d_var_calc)
ma_model_funnel_no_outlier <- rma(ma_data_funnel_no_outlier$d_calc, ma_data_funnel_no_outlier$d_var_calc)

f1<- funnel(ma_model_funnel, xlab = "Effect Size", col = ss_colors) 
legend("topright",bg = "white",legend = c("transitive","intransitive"),pch=16,col=c("red", "blue"))
title(main = "All effect sizes break down by sentence structure")

f2<- funnel(ma_model_funnel_no_outlier, xlab = "Effect Size", col = ss_colors_no_outlier) 
legend("topright",bg = "white",legend = c("transitive","intransitive"),pch=16,col=c("red", "blue"))
title(main = "effect sizes excluded outliers (abs <5) break down by sentence structure")
```

## take int occount sentence structure? 
```{r}
ma_model_sentence_structure <- rma(ma_data_funnel$d_calc~ma_data_funnel$sentence_structure, ma_data_funnel$d_var_calc)
ma_model_no_outlier_ss <- rma(ma_data_funnel_no_outlier$d_calc~ma_data_funnel_no_outlier$sentence_structure, ma_data_funnel_no_outlier$d_var_calc)

f3 <- funnel(ma_model_sentence_structure, xlab = "effect size", col = ss_colors)
f3_b <- funnel(ma_model_no_outlier_ss, xlab = "effect size", col = ss_colors_no_outlier)
```

## take int account sentence structure and age? 
```{r}
ma_model_ss_age <- rma(ma_data_funnel$d_calc~ma_data_funnel$sentence_structure + ma_data_funnel $mean_age, ma_data_funnel$d_var_calc)
ma_model_funnel_no_outlier_ss_age <- rma(ma_data_funnel_no_outlier$d_calc~ma_data_funnel_no_outlier$sentence_structure+ma_data_funnel_no_outlier$mean_age, ma_data_funnel_no_outlier$d_var_calc)



f4 <- funnel(ma_model_ss_age, xlab = "effect size", col = ss_colors)
f4_b <- funnel(ma_model_funnel_no_outlier_ss_age, xlab = "effect size", col = ss_colors_no_outlier)

```

# Variable Summary 
## Continuous Variables
```{r, fig.height =8 }
CONTINUOUS_VARS <- c("n_1", "x_1", "sd_1", "d_calc", "d_var_calc", "mean_age")

long_continuous <- ma_data %>%
  pivot_longer(cols = CONTINUOUS_VARS)

long_continuous %>%
  ggplot(aes(x = value)) +
  geom_histogram() + 
  facet_wrap(~ name, scale = "free_x") +
  labs(title = "Distribution of continuous measures")

long_continuous %>%
  group_by(name) %>%
  summarize(mean = mean(value),
            sd = sd(value)) %>%
  kable()

```  


## Categorical Variables 
```{r, fig.height = 10}
CATEGORICAL_VARS <- c("sentence_structure", "agent_argument_type", "patient_argument_type", "stimuli_actor",
                     "presentation_type", "character_identification",
                     "test_mass_or_distributed", "practice_phase", "test_method")

long_categorical <- ma_data %>%
  pivot_longer(cols = CATEGORICAL_VARS) %>%
  count(name, value) # this is a short cut for group_by() %>% summarize(count = n()) 

long_categorical %>%
  ggplot(aes(x = value, y = n)) +  
  facet_wrap(~ name, scale = "free_x") +
  geom_col(position = 'dodge',width=0.4) + 
  theme(text = element_text(size=8),
        axis.text.x = element_text(angle = 90, hjust = 1))  # rotate x-axis text
```

# Explore Moderators
## no moderators{.tabset}
### all
```{r}
m1 <- rma.mv(d_calc, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m1)
```

### <36
```{r}
ma_data_young <- ma_data %>%
    mutate(age_months = mean_age/30.44) %>% 
    filter(age_months < 36) 

m_young <- rma.mv(d_calc, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
summary(m_young)
```

### >= 36
```{r}
ma_data_old <- ma_data %>%
    mutate(age_months = mean_age/30.44) %>% 
    filter(age_months > 36 | age_months == 36) 

m_old <- rma.mv(d_calc, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
summary(m_old)
```

## age only{.tabset}
### colored by unique_id
```{r}
ma_data %>% 
  ggplot(aes(x = mean_age/30.44, y = d_calc,color = unique_id)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months)") 
```


### all
```{r}
ma_data %>% 
  ggplot(aes(x = mean_age/30.44, y = d_calc, size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_smooth(color = "red") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months)") +
  theme(legend.position = "none") 
```

```{r}
m_age <- rma.mv(d_calc ~ mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age)
```
```{r fig.width = 10, fig.height = 12}
forest(m_age,
       header = T,
       slab = ma_data$unique_id,
       col = "red",
       cex = .7
)

```

```{r}
funnel(m_age)
```

### young, < 36
 
```{r}
ma_data_young %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_smooth(color = "red") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days)") +
  theme(legend.position = "none") 
```

```{r fig.width = 10, fig.height = 12}
m_age_young <- rma.mv(d_calc ~ mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
summary(m_age_young)
```
```{r fig.width = 10, fig.height = 12}
forest(m_age_young,
       header = T,
       slab = ma_data_young$unique_id,
       col = "red",
       cex = .7
)

```


### old, >= 36

```{r}
ma_data_old %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_smooth(color = "red") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days)") +
  theme(legend.position = "none") 
```

```{r}
m_age_old <- rma.mv(d_calc ~ mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
summary(m_age_old)
```




## age and test type {.tabset}
### all 
```{r}
ma_data %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = test_method)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), breakdown my method") 
```
```{r}
m_age_method <- rma.mv(d_calc ~ mean_age + test_method, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_method)
```

## age and sentence structure {.tabset}

### all
```{r}
ma_data %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, , color = sentence_structure)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days)") 
```

```{r}
m_age_sentence <- rma.mv(d_calc ~ mean_age + sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_sentence)
```
Interaction:
```{r}
m_age_sentence <- rma.mv(d_calc ~ mean_age * sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_sentence)
```

### compare transitive vs intransitive 
```{r}
ma_data %>% 
  
```


### < 36, young 
```{r}
ma_data_young_only <- ma_data %>%
    mutate(age_months = mean_age/30.44) %>% 
    filter(age_months < 36) 

ma_data_young_only %>% 
  filter(sentence_structure != "bare_verb") %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1, , color = sentence_structure)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days)") 
```

```{r}
m_age_sentence_young <- rma.mv(d_calc ~ mean_age + sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young_only)
summary(m_age_sentence_young)
```

interaction: 
```{r}
m_age_sentence_young <- rma.mv(d_calc ~ mean_age * sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young_only)
summary(m_age_sentence_young)
```

### >= 36, old 
```{r}
ma_data_old <- ma_data %>%
    mutate(age_months = mean_age/30.44) %>% 
    filter(age_months > 36 | age_months == 36) 

ma_data_old %>% 
  filter(sentence_structure != "bare_verb") %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = sentence_structure)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days)") 
```

```{r}
m_age_sentence_old <- rma.mv(d_calc ~ mean_age + sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
summary(m_age_sentence_old)
```
interaction 
```{r}
m_age_sentence_old <- rma.mv(d_calc ~ mean_age * sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
summary(m_age_sentence_old)
```
## age with stimuli_actor  {.tabset}
### all 
```{r}
ma_data %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = stimuli_actor)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), breakdown by stimuli_actor") 
```

```{r}
m_age_stimuli_actor <- rma.mv(d_calc ~ mean_age + stimuli_actor, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
m_age_stimuli_actor_interaction <- rma.mv(d_calc ~ mean_age * stimuli_actor, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_stimuli_actor)
summary(m_age_stimuli_actor_interaction)
```

### <36, young

```{r}
ma_data_young_only %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = stimuli_actor)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), breakdown by stimuli_actor, young only") 
```

```{r}
m_age_stimuli_actor_young <- rma.mv(d_calc ~ mean_age + stimuli_actor, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young_only)
m_age_stimuli_actor_interaction_young <- rma.mv(d_calc ~ mean_age * stimuli_actor, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young_only)
summary(m_age_stimuli_actor_young)
summary(m_age_stimuli_actor_interaction_young)
```

### >= 36, old 

```{r}
ma_data_old %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = stimuli_actor)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), breakdown by stimuli_actor, old only") 
```

```{r}
m_age_stimuli_actor_old <- rma.mv(d_calc ~ mean_age + stimuli_actor, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
m_age_stimuli_actor_interaction_old <- rma.mv(d_calc ~ mean_age * stimuli_actor, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
summary(m_age_stimuli_actor_old)
summary(m_age_stimuli_actor_interaction_old)
```


## age with presentation_type  {.tabset}
Decided to only compare asynchronous and immediate after:
```{r}
ma_data %>% 
  count(presentation_type)
```

```{r}
ma_data_pt <- ma_data %>% 
  filter(presentation_type != "simultaneous") 

ma_data_pt_young <- ma_data_pt %>% 
  mutate(age_months = mean_age/30.44) %>% 
    filter(age_months < 36) 


ma_data_pt_old <- ma_data_pt %>% 
  mutate(age_months = mean_age/30.44) %>% 
    filter(age_months > 36 | age_months == 36) 

```

### all
```{r}
ma_data_pt %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1,  color = presentation_type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), breakdown by presentation type") 
```

```{r}
m_age_pt <- rma.mv(d_calc ~ mean_age + presentation_type, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_pt)

m_age_pt_interaction <- rma.mv(d_calc ~ mean_age * presentation_type, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_pt)

summary(m_age_pt)
summary(m_age_pt_interaction)
```

### <36, young
```{r}
ma_data_pt_young %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1,  color = presentation_type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), breakdown by presentation type, young only") 
```

```{r}
m_data_pt_young <- rma.mv(d_calc ~ mean_age + presentation_type, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_pt_young)

m_age_pt_interaction_young <- rma.mv(d_calc ~ mean_age * presentation_type, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_pt_young)

summary(m_age_pt)
summary(m_age_pt_interaction)
```

### >= 36, old 
```{r}
ma_data_pt_old %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1,  color = presentation_type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), breakdown by presentation type, young only") 
```

## age with character_identification  {.tabset}
### all 
```{r}
ma_data %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = character_identification)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), breakdown by character_identification") 
```

```{r}
m_age_ci <- rma.mv(d_calc ~ mean_age + character_identification, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
m_age_stimuli_ci_interaction <- rma.mv(d_calc ~ mean_age * character_identification, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_ci)
summary(m_age_stimuli_ci_interaction)
```

### <36, young

```{r}
ma_data_young_only %>% 
  mutate(age_months = mean_age/30.44) %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = character_identification)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), breakdown by character_identification, young only") 
```

```{r}
m_age_ci_young <- rma.mv(d_calc ~ mean_age + character_identification, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young_only)
m_age_ci_interaction_young <- rma.mv(d_calc ~ mean_age * character_identification, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young_only)
summary(m_age_ci_young)
summary(m_age_ci_interaction_young)
```
### >= 36, old 
```{r}
ma_data_old %>% 
  mutate(age_months = mean_age/30.44) %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = character_identification)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), breakdown by character_identification, old only") 
```



## age with practice_phase {.tabset}
### all 
```{r}
ma_data %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = practice_phase)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), breakdown by practice_phase") 
```

```{r}
m_age_pf <- rma.mv(d_calc ~ mean_age + character_identification, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
m_age_pf_interaction <- rma.mv(d_calc ~ mean_age * character_identification, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_ci)
summary(m_age_stimuli_ci_interaction)
```

### <36, young

```{r}
ma_data_young_only %>% 
  mutate(age_months = mean_age/30.44) %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = practice_phase)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), breakdown by practice_phase, young only") 
```

```{r}
m_age_pf_young <- rma.mv(d_calc ~ mean_age + practice_phase, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young_only)
m_age_pf_interaction_young <- rma.mv(d_calc ~ mean_age * practice_phase, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young_only)
summary(m_age_pf_young)
summary(m_age_pf_interaction_young)
```
### >= 36, old 
```{r}
ma_data_old %>% 
  mutate(age_months = mean_age/30.44) %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = practice_phase)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), breakdown by practice_phase, old only") 
```

## age with test_mass_or_distributed {.tabset}
### all 
```{r}
ma_data %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = test_mass_or_distributed)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), breakdown by test type") 
```

```{r}
m_age_tt <- rma.mv(d_calc ~ mean_age + test_mass_or_distributed, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
m_age_tt_interaction <- rma.mv(d_calc ~ mean_age * test_mass_or_distributed, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_tt)
summary(m_age_tt_interaction)
```

### <36, young

```{r}
ma_data_young_only %>% 
  mutate(age_months = mean_age/30.44) %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = test_mass_or_distributed)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), breakdown by test_mass_or_distributed, young only") 
```

```{r}
m_age_tt_young <- rma.mv(d_calc ~ mean_age + test_mass_or_distributed, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young_only)
m_age_tt_interaction_young <- rma.mv(d_calc ~ mean_age * test_mass_or_distributed, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young_only)
summary(m_age_tt_young)
summary(m_age_tt_interaction_young)
```

### >= 36, old 
```{r}
ma_data_old %>% 
  mutate(age_months = mean_age/30.44) %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = test_mass_or_distributed)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), breakdown by test_mass_or_distributed, old only") 
```

## repetition only {.tabset}
### repetition only 
```{r}
ma_data %>% 
  ggplot(mapping = aes(x = n_repetitions_sentence, y = d_calc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("number of repetition per novel verb") +
  ggtitle("Syntactical Bootstrapping effect size vs. number of repetitions for verb") +
  theme_classic() +
  theme(legend.position = "none")

```
```{r}
m_rep <- rma.mv(d_calc ~ n_repetitions_sentence , V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_rep)
```

### repetition only, young 
```{r}
ma_data_young %>% 
  ggplot(mapping = aes(x = n_repetitions_sentence, y = d_calc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("number of repetition per novel verb") +
  ggtitle("Syntactical Bootstrapping effect size vs. number of repetitions for verb") +
  theme_classic() +
  theme(legend.position = "none")
```

```{r}
m_rep_young <- rma.mv(d_calc ~ n_repetitions_sentence , V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
summary(m_rep_young)
```

### repetition only, old 
```{r}
ma_data_old %>% 
  ggplot(mapping = aes(x = n_repetitions_sentence, y = d_calc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("number of repetition per novel verb") +
  ggtitle("Syntactical Bootstrapping effect size vs. number of repetitions for verb") +
  theme_classic() +
  theme(legend.position = "none")
```

```{r}
m_rep_old <- rma.mv(d_calc ~ n_repetitions_sentence , V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
summary(m_rep_old)
```

## repetition with age
### correlation
### all
```{r}
m_rep_age <- rma.mv(d_calc ~ mean_age + n_repetitions_sentence , V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
m_rep_age_interaction <- rma.mv(d_calc ~ mean_age*n_repetitions_sentence , V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_rep_age)
summary(m_rep_age_interaction)

```

### young, <36
```{r}
m_rep_age_young <- rma.mv(d_calc ~ mean_age + n_repetitions_sentence , V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
m_rep_age_interaction_young <- rma.mv(d_calc ~ mean_age*n_repetitions_sentence , V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
summary(m_rep_age_young)
summary(m_rep_age_interaction_young)

```


### old > 36
```{r}
m_rep_age_old <- rma.mv(d_calc ~ mean_age + n_repetitions_sentence , V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
m_rep_age_interaction_old <- rma.mv(d_calc ~ mean_age*n_repetitions_sentence , V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
summary(m_rep_age_old)
summary(m_rep_age_interaction_old)

```



## vocab {.tabset}
### vocab (median)
```{r}
ma_data_with_vocab <- ma_data %>% 
  mutate(vocab = case_when(!is.na(productive_vocab_median) ~ productive_vocab_median,
                           !is.na(productive_vocab_mean) ~ productive_vocab_mean,
                            TRUE ~ NA_real_),
         vocab_source = case_when(!is.na(productive_vocab_median) ~ "median",
                           !is.na(productive_vocab_mean) ~ "mean",
                            TRUE ~ NA_character_)) 

ma_data_with_vocab %>%
  ggplot(aes(x = productive_vocab_median, y = d_calc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic()
```

```{r}
m_vocab <- rma.mv(d_calc ~ productive_vocab_median, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_with_vocab)
summary(m_vocab)
```


### age comparison 
```{r}
ma_data_with_vocab_age <- ma_data_with_vocab %>% 
  filter(vocab_source == "median" &
        !is.na(vocab)) 

ma_data_with_vocab_age %>% 
  ggplot(aes(x = mean_age, y = d_calc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic()
  
```

```{r}
m_age_with_vocab <- rma.mv(d_calc ~ mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_with_vocab_age)
summary(m_age_with_vocab)
```

### < 36, young
```{r}
ma_data_with_vocab_age_young <- ma_data_with_vocab_age %>% 
  mutate(age_months = mean_age/30.44) %>% 
  filter(age_months < 36) 


ma_data_with_vocab_age_young %>% 
  ggplot(aes(x = productive_vocab_median, y = d_calc, size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. vocab (months)") 
    
```

```{r WORKING}

CATEGORICAL_VARS <- c("sentence_structure", "agent_argument_type", "patient_argument_type", "stimuli_actor",
                     "presentation_type", "character_identification",
                     "test_mass_or_distributed", "practice_phase", "test_method")


ma_data %>% filter(!is.na(mean_age)) %>% summarize(mean_age = mean(mean_age)) 

ma_data_ageExpl <- ma_data %>% mutate(AGE_group = (if_else(mean_age > 915.22, "OLD", "YOUNG")))
 

ggplot(ma_data_ageExpl, aes(x = sentence_structure, 
                    y = d_calc, 
                    group = presentation_type, 
                    color = presentation_type
                   )) +
  geom_line() +
  geom_point(position = "jitter") +
  geom_point(alpha = .4)  +
  ylab("Effect Size") +
  xlab("Sentence Structure") +
  ggtitle("ME effect size by Sentence Structure") 

ggplot(ma_data_ageExpl, aes(x = sentence_structure, 
                    y = d_calc, 
                    group = unique_id, 
                    color = unique_id
                   )) + 
  geom_line() +
  geom_point(position = "jitter") +
  geom_point(alpha = .4)  +
  ylab("Effect Size") +
  xlab("Sentence Structure") +
  ggtitle("ME effect size by Sentence Structure") 

```
```{r}
ma_data %>% 
  group_by(agent_argument_type_clean) %>% count
```

```{r}
ggplot(ma_data, aes(x = agent_argument_type_clean, 
                    y = d_calc, 
                    color = agent_argument_type_clean)) +
  geom_violin() +
  geom_point(alpha = .4)  +
  ylab("Effect Size") +
  xlab("Response Mode") +
  ggtitle("ME effect size by Response mode") +
  theme_classic() +
  theme(legend.position = "none")

cis_by_aa <- ma_data %>%
    group_by(agent_argument_type_clean) %>%
    summarize(mean = mean(d_calc),
            sd = sd(d_calc),
            n = n()) %>%
    mutate(ci_range_95 =  1.96 * (sd/sqrt(n)),
         ci_lower = mean - ci_range_95,
         ci_upper = mean + ci_range_95)

#pdf("plots/moderator_plot1.pdf", height = 6, width = 6)

ggplot(ma_data, aes(x = agent_argument_type_clean, 
                    y = d_calc, 
                    color = agent_argument_type_clean)) +
  geom_violin() +
  geom_point(alpha = .4)  +
  ylab("Effect Size") +
  xlab("Response Mode") +
  ggtitle("ME effect size by Response mode") +
  geom_pointrange(data = cis_by_aa, 
                  aes(x = agent_argument_type_clean, 
                      y = mean, ymin = ci_lower, 
                      ymax = ci_upper), 
                  color = "black") +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  theme_classic(base_size = 16) +
  theme(legend.position = "none")
```



### < 36, young, age comparison
```{r}

ma_data_with_vocab_age_young %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months)") 
    
```

```{r}
m_age_with_vocab_young <- rma.mv(d_calc ~ mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_with_vocab_age_young)
summary(m_age_with_vocab)
```
### correlationt est
```{r}
cor.test(ma_data_with_vocab$mean_age,
         ma_data_with_vocab$productive_vocab_median)
```



