---
title: "Syntactic Boostrapping MA - agent"
subtitle: "Data V3!!"
author: "Anjie Cao and Molly Lewis"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc_float: yes
    code_folding: hide 
    number_sections: no
    toc: yes
---


```{r setup, include = F}
library(glue)
library(tidyverse)
library(googlesheets4)
library(metafor)
library(knitr)
library(gridExtra)
library(here)
library(dict)
library(heatmaply)
library(MuMIn)
library(glmulti)
GOOGLE_SHEET_ID <- "1kSL5lpmHcaw9lOp2dhJ_RH15REFe7oZVwMO1vJc930o"
```



```{r GlobalOptions}
options(knitr.duplicate.label = 'allow')
```

```{r global_options, include=FALSE}


knitr::opts_chunk$set(fig.height=6, fig.path='Figs/',
                     warning=FALSE, message=FALSE)
theme_set(theme_classic()) # sets global plot theme
```

```{r}
DATA_PATH <- here("data/processed/syntactic_bootstrapping_tidy_data.csv") # make all variables (i.e. things that might change) as capital letters at the top of the scripts

ma_data <- read_csv(DATA_PATH) 
ma_data <- ma_data %>% filter(paradigm_type != "action_matching")
```



# Data Overview {.tabset}
## effect size & paper 
```{r}
n_effect_sizes <- ma_data %>%
  filter(!is.na(d_calc)) %>%
  nrow()

n_papers <- ma_data %>%
  distinct(unique_id) %>%
  nrow()

```

There are `r n_effect_sizes` effect sizes collected from `r n_papers` different papers.

Here are the papers in this analysis:
```{r}
ma_data %>%
  count(short_cite) %>%
  arrange(-n) %>%
  DT::datatable()
```
## Forest plot 
```{r}
ma_model <- rma(ma_data$d_calc, ma_data$d_var_calc)
ma_model
forest(ma_model,
       header = T,
       slab = ma_data$unique_id,
       col = "red",
       cex = .7)

```
## funnel plot {.tabset}
### vanilla 
```{r}

ma_data %>% 
  mutate(color = ifelse(sentence_structure == "transitive", "red", "blue"),
         color_sample_size = ifelse(n_1 < 10, "red", ifelse(n_1 < 20, "orange", "yellow")),
         color_confidence = ifelse(inclusion_certainty == 1, "red", "black"))-> ma_data_funnel


ma_data_funnel %>% filter (abs(d_calc) < 5) -> ma_data_funnel_no_outlier

ss_colors <- ma_data_funnel$color
ss_colors_no_outlier <- ma_data_funnel_no_outlier$color 

ma_model_funnel <- rma(ma_data_funnel$d_calc, ma_data_funnel$d_var_calc)
ma_model_funnel_no_outlier <- rma(ma_data_funnel_no_outlier$d_calc, ma_data_funnel_no_outlier$d_var_calc)

f1<- funnel(ma_model_funnel, xlab = "Effect Size", col = ss_colors) 
legend("topright",bg = "white",legend = c("transitive","intransitive"),pch=16,col=c("red", "blue"))
title(main = "All effect sizes break down by sentence structure")

f2<- funnel(ma_model_funnel_no_outlier, xlab = "Effect Size", col = ss_colors_no_outlier) 
legend("topright",bg = "white",legend = c("transitive","intransitive"),pch=16,col=c("red", "blue"))
title(main = "effect sizes excluded outliers (abs <5) break down by sentence structure")
```

### take into account sentence structure? 
```{r}
ma_model_sentence_structure <- rma(ma_data_funnel$d_calc~ma_data_funnel$sentence_structure, ma_data_funnel$d_var_calc)
ma_model_no_outlier_ss <- rma(ma_data_funnel_no_outlier$d_calc~ma_data_funnel_no_outlier$sentence_structure, ma_data_funnel_no_outlier$d_var_calc)

f3 <- funnel(ma_model_sentence_structure, xlab = "effect size", col = ss_colors)
f3_b <- funnel(ma_model_no_outlier_ss, xlab = "effect size", col = ss_colors_no_outlier)
```

### take into account sentence structure and age? 
```{r}
ma_model_ss_age <- rma(ma_data_funnel$d_calc~ma_data_funnel$sentence_structure + ma_data_funnel $mean_age, ma_data_funnel$d_var_calc)
ma_model_funnel_no_outlier_ss_age <- rma(ma_data_funnel_no_outlier$d_calc~ma_data_funnel_no_outlier$sentence_structure+ma_data_funnel_no_outlier$mean_age, ma_data_funnel_no_outlier$d_var_calc)



f4 <- funnel(ma_model_ss_age, xlab = "effect size", col = ss_colors)
f4_b <- funnel(ma_model_funnel_no_outlier_ss_age, xlab = "effect size", col = ss_colors_no_outlier)

```


# Variable Summary 
## Continuous Variables
```{r, fig.height =8 }
CONTINUOUS_VARS <- c("n_1", "x_1", "sd_1", "d_calc", "d_var_calc", "mean_age","n_train_test_pair","n_test_trial_per_pair","productive_vocab_mean", "productive_vocab_median")

long_continuous <- ma_data %>%
  pivot_longer(cols = CONTINUOUS_VARS)

long_continuous %>%
  ggplot(aes(x = value)) +
  geom_histogram() + 
  facet_wrap(~ name, scale = "free_x") +
  labs(title = "Distribution of continuous measures")

long_continuous %>%
  group_by(name) %>%
  summarize(mean = mean(value),
            sd = sd(value)) %>%
  kable()

```  


## Categorical Variables 
```{r, fig.height = 10}
CATEGORICAL_VARS <- c("sentence_structure", "agent_argument_type_clean", "patient_argument_type_clean", "stimuli_actor","agent_argument_number","transitive_event_type","intransitive_event_type",
                     "presentation_type", "character_identification",
                     "test_mass_or_distributed", "practice_phase", "test_method")

long_categorical <- ma_data %>%
  pivot_longer(cols = CATEGORICAL_VARS) %>%
  count(name, value) # this is a short cut for group_by() %>% summarize(count = n()) 

long_categorical %>%
  ggplot(aes(x = value, y = n)) +  
  facet_wrap(~ name, scale = "free_x") +
  geom_col(position = 'dodge',width=0.4) + 
  theme(text = element_text(size=8),
        axis.text.x = element_text(angle = 90, hjust = 1))  # rotate x-axis text
```

## Prep for Moderators
```{r seperation}

ma_data_young <- ma_data_young <- ma_data %>%
    mutate(age_months = mean_age/30.44) %>% 
    filter(age_months < 36) 

ma_data_old <-  ma_data %>%
    mutate(age_months = mean_age/30.44) %>% 
    filter(age_months > 36 | age_months == 36) 

ma_data_vocab <- ma_data %>%
    filter(!is.na(productive_vocab_median)) 

```
## no moderators{.tabset}
### all
```{r}
m1 <- rma.mv(d_calc, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m1)
```

### <36
```{r}
m_young <- rma.mv(d_calc, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
summary(m_young)
```

### >= 36
```{r}

m_old <- rma.mv(d_calc, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
summary(m_old)
```


# Participants characteristics:

## age only{.tabset}
### colored by unique_id


```{r plot_age_unique_id}
ma_data %>% 
  ggplot(aes(x = mean_age/30.44, y = d_calc,color = unique_id)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months)") 
```


### all
```{r plot_age}
ma_data %>% 
  ggplot(aes(x = mean_age/30.44, y = d_calc, size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_smooth(color = "red") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months)") +
  theme(legend.position = "none") 
```

```{r simple_model_age}
m_simple <- rma.mv(d_calc ~ 1, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)

m_age <- rma.mv(d_calc ~ mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_simple)
summary(m_age)

```


```{r fig.width = 10, fig.height = 12}
forest(m_age,
       header = T,
       slab = ma_data$unique_id,
       col = "red",
       cex = .7
)

```

```{r funne_plot}
funnel(m_age)
```

### young, < 36
 
```{r plot_age_young}
ma_data_young %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_smooth(color = "red") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months)") +
  theme(legend.position = "none") 
```

```{r simple_model_age_young}
m_age_young <- rma.mv(d_calc ~ mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
summary(m_age_young)
```
```{r fig.width = 10, fig.height = 12}
forest(m_age_young,
       header = T,
       slab = ma_data_young$unique_id,
       col = "red",
       cex = .7
)

```


### old, >= 36

```{r plot_age_old}
ma_data_old %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_smooth(color = "red") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months)") +
  theme(legend.position = "none") 
```

```{r simple_model_age_old}
m_age_old <- rma.mv(d_calc ~ mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
summary(m_age_old)
```
## vocab 
```{r plot_vocab}
ma_data_vocab %>%
  ggplot(aes(x = productive_vocab_median, y = d_calc, size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_smooth(color = "red") +
  ylab("Effect Size") +
  xlab("Median Vocabulary Size") +
  ggtitle("Syntactical Bootstrapping effect size vs. Median Vocabulary (months)") +
  theme(legend.position = "none") 

```

```{r simple_model_vocab}
m_age_vocab <- rma.mv(d_calc ~ productive_vocab_median, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab)
summary(m_age_vocab)
```

```{r simple_model_vocab_a}
m_vocab_with_age <- rma.mv(d_calc ~ mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab)
summary(m_vocab_with_age)
```

# Linguistic Stimuli 

## Sentence structure {.tabset}

### all with age
```{r plot_age_ss}
ma_data %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = sentence_structure)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months)") 
```
```{r simple_model_ss}
m_age_sentence <- rma.mv(d_calc ~ mean_age + sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_sentence)
```
```{r interaction_model_ss}
m_age_sentence <- rma.mv(d_calc ~ mean_age * sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_sentence)
```

### < 36, young, age
```{r plot_age_ss_young}

ma_data_young %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, , color = sentence_structure)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), with sentence_structure") 
```

```{r simple_model_age_ss_young}
m_age_sentence_young <- rma.mv(d_calc ~ mean_age + sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
summary(m_age_sentence_young)
```

```{r interaction_model_age_ss_young}
m_age_sentence_young <- rma.mv(d_calc ~ mean_age * sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
summary(m_age_sentence_young)
```

### >= 36, old, age 
```{r plot_age_ss_old}
ma_data_old %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = sentence_structure)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months)") 
```
```{r simple_model_age_ss_old}
m_age_sentence_old <- rma.mv(d_calc ~ mean_age + sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
summary(m_age_sentence_old)
```
```{r interaction_model_age_ss_old} 
m_age_sentence_old_interaction <- rma.mv(d_calc ~ mean_age * sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
summary(m_age_sentence_old)
```

### all with vocab
```{r plot_ss_vocab}
ma_data_vocab %>% 
  ggplot(aes(x = productive_vocab_median, y = d_calc, size = n_1, color = sentence_structure)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Median Productive Vocab") +
  ggtitle("Syntactical Bootstrapping effect size vs. Median Productive Vocab")
```

<!-- ```{r simple_model_ss_vocab} -->
<!-- m_age_sentence_vocab <- rma.mv(d_calc ~ productive_vocab_median + sentence_structure, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_vocab) -->
<!-- summary(m_age_sentence_vocab) -->
<!-- ``` -->

<!-- ```{r interaction_model_ss_vocab} -->
<!-- m_age_sentence_vocab_interaction <- rma.mv(d_calc ~ productive_vocab_median * sentence_structure, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_vocab) -->
<!-- summary(m_age_sentence_vocab) -->
<!-- ``` -->

## Agent Arguement Type (Noun, pronoun and varying) {.tabset}
decide to compare noun, pronoun and varying 
```{r count_number_and_seperation_AAT}
ma_data %>% group_by(agent_argument_type_clean) %>% count()
ma_data_at <- ma_data %>% filter(agent_argument_type_clean != "noun_phrase")
ma_data_at_young <- ma_data_at %>%
    mutate(age_months = mean_age/30.44) %>% 
    filter(age_months < 36) 
ma_data_at_old <- ma_data_at %>%
    mutate(age_months = mean_age/30.44) %>% 
    filter(age_months > 36 | age_months == 36) 
ma_data_at_vocab <- ma_data_at %>%
      filter(!is.na(productive_vocab_median)) 

```
### all 
```{r plot_age_aat}
ma_data_at %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = agent_argument_type_clean)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by agent argument") 
```
```{r simple_model_age_aat}
m_age_aa <- rma.mv(d_calc ~ mean_age + agent_argument_type_clean, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_at)
summary(m_age_aa)
```
```{r interaction_model_age_aat}
m_age_aa_interaction <- rma.mv(d_calc ~ mean_age * agent_argument_type_clean, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_at)
summary(m_age_aa_interaction)
```

### <36, young 
```{r plot_age_aat_young}
ma_data_at_young %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = agent_argument_type_clean)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by agent argument, young only") 
  
```
```{r simple_model_age_aat_young}
m_age_aa_young <- rma.mv(d_calc ~ mean_age + agent_argument_type_clean, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_at_young)
summary(m_age_aa_young)
```

```{r interaction_model_age_young}
m_age_aa_young_interaction <- rma.mv(d_calc ~ mean_age * agent_argument_type_clean, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_at_young)
summary(m_age_aa_young_interaction)
```

### >=36, old 
```{r plot_age_aat_old}
ma_data_at_old %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = agent_argument_type_clean)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by agent argument, young only") 
  
```

# ```{r simple_model_age_aat_old}
# m_age_aa_old <- rma.mv(d_calc ~ mean_age + agent_argument_type_clean, V = d_var_calc,
#                             random = ~ 1 | short_cite, data = ma_data_at_old)
# summary(m_age_aa_old)
# ```
# ```{r interaction_model_age_old}
# m_age_aa_old_interaction <- rma.mv(d_calc ~ mean_age * agent_argument_type_clean, V = d_var_calc,
#                             random = ~ 1 | short_cite, data = ma_data_at_old)
# summary(m_age_aa_old_interaction)
# ```

### Vocab 
```{r plot_vocab_aat}
ma_data_at_vocab %>% 
  ggplot(aes(x = productive_vocab_median, y = d_calc, size = n_1, color = agent_argument_type_clean)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by agent argument, with vocab") 
  
```

```{r simple_model_plot_vocab_aat_old}
m_age_aa_vocab <- rma.mv(d_calc ~ productive_vocab_median + agent_argument_type_clean, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_at_vocab)
summary(m_age_aa_vocab)
```

```{r interaction_model_plot_vocab_aat_old}
m_age_aa_vocab_interaction <- rma.mv(d_calc ~ productive_vocab_median * agent_argument_type_clean, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_at_vocab)
summary(m_age_aa_vocab_interaction)
```

## Patient Argument Type (??) 
```{r count_PAT}
ma_data %>% group_by(patient_argument_type_clean) %>% count()
```

## Agent Argument Numbers (??)
```{r count_AAN}
ma_data %>% group_by(agent_argument_number) %>% count()
```

## Number of sentence reptition {.tabset}
```{r summary_plot_SR}
ma_data %>% ggplot(aes(x = n_repetitions_sentence)) +
  geom_histogram() 
```
### all
```{r plot_SR}
ma_data %>% 
  ggplot(aes(x = n_repetitions_sentence, y = d_calc, size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("number of reptition in sentence") +
  ggtitle("Syntactical Bootstrapping effect size vs. number of sentence repetition") 
  
```

```{r simple_model_SR}
m_rep <- rma.mv(d_calc ~ n_repetitions_sentence, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_rep)
```

```{r simple_model_SR_age}
m_rep_age <- rma.mv(d_calc ~ n_repetitions_sentence + mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_rep_age)
```

```{r interaction_model_SR_age}
m_rep_age_interaction <- rma.mv(d_calc ~ n_repetitions_sentence * mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_rep_age_interaction)
```

### < 36, young only 
```{r plot_SR_young}
ma_data_young %>% 
  ggplot(aes(x = n_repetitions_sentence, y = d_calc, size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("number of reptition in sentence") +
  ggtitle("Syntactical Bootstrapping effect size vs. number of sentence repetition, young only") 
```

```{r simple_model_SR_young}
m_rep_young <- rma.mv(d_calc ~ n_repetitions_sentence, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
summary(m_rep_young)
```

```{r simple_model_SR_age_young}
m_rep_age_young <- rma.mv(d_calc ~ n_repetitions_sentence + mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
summary(m_rep_age_young)
```

```{r interaction_model_SR_age_young}
m_rep_age_interaction_young <- rma.mv(d_calc ~ n_repetitions_sentence * mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
summary(m_rep_age_interaction_young)
```

### >= 36, old only
```{r plot_SR_old}
ma_data_old %>% 
  ggplot(aes(x = n_repetitions_sentence, y = d_calc, size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("number of reptition in sentence") +
  ggtitle("Syntactical Bootstrapping effect size vs. number of sentence repetition, old only") 
```

```{r simple_model_SR_old}
m_rep_old <- rma.mv(d_calc ~ n_repetitions_sentence, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
summary(m_rep_old)
```

```{r simple_model_SR_age_old}
m_rep_age_old <- rma.mv(d_calc ~ n_repetitions_sentence + mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
summary(m_rep_age_old)
```

```{r interaction_model_SR_age_old}
m_rep_age_interaction_old <- rma.mv(d_calc ~ n_repetitions_sentence * mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
summary(m_rep_age_interaction_old)
```

### add vocab in 
```{r vocab_SR_simple}
m_rep_v_r <- rma.mv(d_calc ~ n_repetitions_sentence + productive_vocab_median, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab)
summary(m_rep_v_r)
```

```{r vocab_SR_interaction}
m_rep_v_r_interaction <- rma.mv(d_calc ~ n_repetitions_sentence *productive_vocab_median, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab)
summary(m_rep_v_r)
```

# Visual stimuli  

## stimuli_modality(video vs animation) {.tabset}

### all
```{r plot_StMo}
ma_data %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = stimuli_modality)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by stimuli modality") 
```

```{r simple_model_StMo}
m_stim_mod<- rma.mv(d_calc ~ mean_age + stimuli_modality, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_stim_mod)

```

```{r interaction_model_StMo}
m_stim_mod_interaction<- rma.mv(d_calc ~ mean_age * stimuli_modality, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_stim_mod_interaction)
```

### < 36, young only 
```{r plot_StMo_young}
ma_data_young %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = stimuli_modality)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by stimuli modality, young") 
```

```{r simple_model_StMo_young}
m_stim_mod_young<- rma.mv(d_calc ~ mean_age + stimuli_modality, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
summary(m_stim_mod_young)

```

```{r interaction_model_StMo_young}
m_stim_mod_interaction_young <- rma.mv(d_calc ~ mean_age * stimuli_modality, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
summary(m_stim_mod_interaction_young)
```

### >= 36, old only
```{r plot_StMo_old}
ma_data_old %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = stimuli_modality)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by stimuli modality, old") 
```

<!-- ```{r simple_model_StMo_old} -->
<!-- m_stim_mod_old<- rma.mv(d_calc ~ mean_age + stimuli_modality, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_old) -->
<!-- summary(m_stim_mod_old) -->

<!-- ``` -->

<!-- ```{r interaction_model_StMo_old} -->
<!-- m_stim_mod_interaction_old <- rma.mv(d_calc ~ mean_age * stimuli_modality, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_old) -->
<!-- summary(m_stim_mod_interaction_old) -->
<!-- ``` -->

### vocab 
```{r plot_StMo_vocab}
ma_data_vocab %>% 
  ggplot(aes(x = productive_vocab_median, y = d_calc, size = n_1, color = stimuli_modality)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("median vocab") +
  ggtitle("Syntactical Bootstrapping effect size vs. median vocab, breakdown by stimuli modality, vocab") 

```

```{r simple_model_StMo_vocab}
m_stim_mod_v <- rma.mv(d_calc ~ productive_vocab_median + stimuli_modality, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab)
summary(m_stim_mod_v)

```

```{r interaction_model_StMo_vocab}
m_stim_mod_intereaction_v <- rma.mv(d_calc ~ productive_vocab_median * stimuli_modality, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab)
summary(m_stim_mod_intereaction_v)
```

### vocab age comparison
```{r plot_StMo_vocab_a}
ma_data_vocab %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = stimuli_modality)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by stimuli modality, age compare vocab") 

```

```{r simple_model_StMo_vocab_a}
m_stim_mod_v_a<- rma.mv(d_calc ~ mean_age + stimuli_modality, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab)
summary(m_stim_mod_v_a)

```

```{r interaction_model_StMo_vocab_a}
m_stim_mod_interaction_v_a <- rma.mv(d_calc ~ mean_age * stimuli_modality, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab)
summary(m_stim_mod_interaction_v_a)
```

## stimuli_actor (person vs non-person) {.tabset}
### all
```{r plot_StAc}
ma_data %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = stimuli_actor)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by stimuli actor, all") 


```

```{r simple_model_StAc}
m_stim_actor_age <- rma.mv(d_calc ~ mean_age + stimuli_actor, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)

summary(m_stim_actor_age)

```

```{r interaction_model_StAc}
m_stim_actor_age_interaction <- rma.mv(d_calc ~ mean_age * stimuli_actor, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)

summary(m_stim_actor_age_interaction)

```

### < 36, young only 
```{r plot_StAc_young}
ma_data_young %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = stimuli_actor)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by stimuli actor, young") 

```

```{r simple_model_StAc_young}
m_stim_actor_age_young <- rma.mv(d_calc ~ mean_age + stimuli_actor, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)

summary(m_stim_actor_age_young)

```

```{r interaction_model_young}
m_stim_actor_age_interaction_young <- rma.mv(d_calc ~ mean_age * stimuli_actor, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)

summary(m_stim_actor_age_interaction_young)

```

### >= 36, old only
```{r plot_StAc_old}
ma_data_old %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = stimuli_actor)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by stimuli actor, old") 

```

```{r simple_model_StAc_old}
m_stim_actor_age_old <- rma.mv(d_calc ~ mean_age + stimuli_actor, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)

summary(m_stim_actor_age_old)

```

```{r interaction_model_old}
m_stim_actor_age_interaction_old <- rma.mv(d_calc ~ mean_age * stimuli_actor, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)

summary(m_stim_actor_age_interaction_old)

```

### vocab 
```{r plot_StAc_vocab}
ma_data_vocab %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = productive_vocab_median, y = d_calc, size = n_1, color = stimuli_actor)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by stimuli actor, vocab") 


```

```{r simple_model_StAc_vocab}
m_stim_actor_vocab <- rma.mv(d_calc ~ productive_vocab_median + stimuli_actor, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab)

summary(m_stim_actor_vocab)

```

```{r interaction_model_vocab}
m_stim_actor_vocab_interaction <- rma.mv(d_calc ~ productive_vocab_median * stimuli_actor, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab)

summary(m_stim_actor_vocab_interaction)
```

### vocab age comparison
```{r plot_StAc_vocab_a}
ma_data_vocab %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = stimuli_actor)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by stimuli actor, age vocab comparison") 


```

```{r simple_model_StAc_vocab_a}
m_stim_actor_vocab_a <- rma.mv(d_calc ~ mean_age + stimuli_actor, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab)

summary(m_stim_actor_vocab_a)

```

```{r interaction_model_vocab_a}
m_stim_actor_vocab_interaction_a <- rma.mv(d_calc ~ mean_age * stimuli_actor, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab)

summary(m_stim_actor_vocab_interaction_a)
```

## transitive_event (indirect_caused_action vs direct caused action) {.tabset}
```{r summary_seperate_TE}


ma_data %>% count(transitive_event_type)

m_data_transtivity <- ma_data %>% 
  filter(transitive_event_type != "minimal_contact") 

m_data_transtivity_young <- ma_data %>% 
  filter(transitive_event_type != "minimal_contact") %>% 
  mutate(age_months = mean_age/30.44) %>% 
  filter(age_months < 36) 

m_data_transtivity_old <- ma_data %>% 
  filter(transitive_event_type != "minimal_contact") %>% 
  mutate(age_months = mean_age/30.44) %>% 
  filter(age_months > 36 | age_months == 36) 

m_data_transitivity_vocab <- ma_data_vocab %>% 
    filter(transitive_event_type != "minimal_contact") 

  

```
### all 
```{r plot_TE}
m_data_transtivity %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = transitive_event_type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by transitive_event_type") 
```

<!-- ```{r simple_model_TE} -->
<!-- m_age_vs_tran <- rma.mv(d_calc ~ mean_age + transitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_transtivity) -->

<!-- summary(m_age_vs_tran) -->
<!-- ``` -->

<!-- ```{r interaction_model_TE} -->
<!-- m_data_transtivity_interaction <- rma.mv(d_calc ~ mean_age * transitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_transtivity) -->
<!-- summary(m_data_transtivity_interaction) -->
<!-- ``` -->

<!-- ### young < 36 -->
<!-- ```{r plot_TE_young} -->
<!-- m_data_transtivity_young %>%  -->
<!--   mutate(age_months = mean_age/30.44) %>%  -->
<!--   ggplot(aes(x = age_months, y = d_calc, size = n_1, color = transitive_event_type)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm") + -->
<!--   ylab("Effect Size") + -->
<!--   xlab("Age (months)") + -->
<!--   ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by transitive_event_type")  -->
<!-- ``` -->

<!-- ```{r simple_model_TE_young} -->
<!-- m_age_vs_tran_young <- rma.mv(d_calc ~ mean_age + transitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_transtivity_young) -->

<!-- summary(m_age_vs_tran_young) -->
<!-- ``` -->

<!-- ```{r interaction_model_TE_young} -->
<!-- m_data_transtivity_interaction_young <- rma.mv(d_calc ~ mean_age * transitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_transtivity_young) -->
<!-- summary(m_data_transtivity_interaction_young) -->
<!-- ``` -->

<!-- ### old > 36 -->
<!-- ```{r plot_TE_old} -->
<!-- m_data_transtivity_old %>%  -->
<!--   mutate(age_months = mean_age/30.44) %>%  -->
<!--   ggplot(aes(x = age_months, y = d_calc, size = n_1, color = transitive_event_type)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm") + -->
<!--   ylab("Effect Size") + -->
<!--   xlab("Age (months)") + -->
<!--   ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by transitive_event_type")  -->
<!-- ``` -->

<!-- ```{r simple_model_TE_old} -->
<!-- m_age_vs_tran_old <- rma.mv(d_calc ~ mean_age + transitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_transtivity_old) -->

<!-- summary(m_age_vs_tran_old) -->
<!-- ``` -->

<!-- ```{r interaction_model_TE_old} -->
<!-- m_data_transtivity_interaction_old <- rma.mv(d_calc ~ mean_age * transitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_transtivity_old) -->
<!-- summary(m_data_transtivity_interaction_old) -->
<!-- ``` -->

<!-- ### vocab  -->
<!-- ```{r plot_TE_vocab} -->
<!-- m_data_transitivity_vocab %>%  -->
<!--   mutate(age_months = mean_age/30.44) %>%  -->
<!--   ggplot(aes(x = productive_vocab_median, y = d_calc, size = n_1, color = transitive_event_type)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm") + -->
<!--   ylab("Effect Size") + -->
<!--   xlab("median vocab") + -->
<!--   ggtitle("Syntactical Bootstrapping effect size vs. median vocab, breakdown by transitive_event_type")  -->
<!-- ``` -->

<!-- ```{r simple_model_TE_vocab} -->
<!-- m_age_vs_tran_vocab <- rma.mv(d_calc ~ productive_vocab_median + transitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_transitivity_vocab) -->

<!-- summary(m_age_vs_tran_old) -->
<!-- ``` -->

<!-- ```{r interaction_model_TE_vocab } -->
<!-- m_data_transtivity_interaction_vocab <- rma.mv(d_calc ~ productive_vocab_median * transitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_transitivity_vocab) -->
<!-- summary(m_data_transtivity_interaction_vocab) -->
<!-- ``` -->

<!-- ### vocab age comparsion  -->

<!-- ```{r plot_TE_vocab_a} -->
<!-- m_data_transitivity_vocab %>%  -->
<!--   mutate(age_months = mean_age/30.44) %>%  -->
<!--   ggplot(aes(x = mean_age, y = d_calc, size = n_1, color = transitive_event_type)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm") + -->
<!--   ylab("Effect Size") + -->
<!--   xlab("Age (months)") + -->
<!--   ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by transitive_event_type")  -->
<!-- ``` -->

<!-- ```{r simple_model_TE_vocab_a} -->
<!-- m_age_vs_tran_vocab <- rma.mv(d_calc ~ mean_age + transitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_transitivity_vocab) -->

<!-- summary(m_age_vs_tran_old) -->
<!-- ``` -->

<!-- ```{r interaction_model_TE_vocab_a} -->
<!-- m_data_transtivity_interaction_vocab <- rma.mv(d_calc ~ mean_age * transitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_transitivity_vocab) -->
<!-- summary(m_data_transtivity_interaction_vocab) -->
<!-- ``` -->


## intransitive_event (one vs parallel) {.tabset}
```{r summary_and_seperate_ITE}
ma_data %>% count(intransitive_event_type) 

m_data_intran <- ma_data %>% 
  filter(intransitive_event_type != "minimal_contact") 

m_data_intran_young <- ma_data %>% 
  filter(intransitive_event_type != "minimal_contact") %>% 
  mutate(age_months = mean_age/30.44) %>% 
  filter(age_months < 36) 

m_data_intran_old <- ma_data %>% 
  filter(intransitive_event_type != "minimal_contact") %>% 
  mutate(age_months = mean_age/30.44) %>% 
  filter(age_months > 36 | age_months == 36) 

m_data_intran_vocab <- ma_data_vocab %>% 
    filter(intransitive_event_type != "minimal_contact") 
```
### all 
```{r plot_ITE}
m_data_intran %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = intransitive_event_type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by intransitive_event_type") 
```

<!-- ```{r simple_model_ITE} -->
<!-- m_age_vs_intran <- rma.mv(d_calc ~ mean_age + intransitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_intran) -->

<!-- summary(m_age_vs_intran) -->
<!-- ``` -->

<!-- ```{r interaction_model_ITE } -->
<!-- m_data_intranstivity_interaction <- rma.mv(d_calc ~ mean_age * intransitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_intran) -->
<!-- summary(m_data_intranstivity_interaction) -->
<!-- ``` -->

<!-- ### young < 36 -->
<!-- ```{r plot_ITE_young} -->
<!-- m_data_intran_young %>%  -->
<!--   mutate(age_months = mean_age/30.44) %>%  -->
<!--   ggplot(aes(x = age_months, y = d_calc, size = n_1, color = intransitive_event_type)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm") + -->
<!--   ylab("Effect Size") + -->
<!--   xlab("Age (months)") + -->
<!--   ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by intransitive_event_type, young")  -->
<!-- ``` -->

<!-- ```{r simple_model_ITE_young} -->
<!-- m_age_vs_intran_young <- rma.mv(d_calc ~ mean_age + intransitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_intran_young) -->

<!-- summary(m_age_vs_intran_young) -->
<!-- ``` -->

<!-- ```{r interaction_model_ITE_young} -->
<!-- m_data_intranstivity_interaction_young <- rma.mv(d_calc ~ mean_age * intransitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_intran_young) -->
<!-- summary(m_data_intranstivity_interaction_young) -->
<!-- ``` -->

<!-- ### old > 36 -->
<!-- ```{r plot_ITE_old} -->
<!-- m_data_intran_old %>%  -->
<!--   mutate(age_months = mean_age/30.44) %>%  -->
<!--   ggplot(aes(x = age_months, y = d_calc, size = n_1, color = intransitive_event_type)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm") + -->
<!--   ylab("Effect Size") + -->
<!--   xlab("Age (months)") + -->
<!--   ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by intransitive_event_type, old")  -->
<!-- ``` -->

<!-- ```{r simple_model_ITE_old} -->
<!-- m_age_vs_intran_old <- rma.mv(d_calc ~ mean_age + intransitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_intran_old) -->

<!-- summary(m_age_vs_intran_old) -->
<!-- ``` -->

<!-- ```{r interaction_model_ITE_old} -->
<!-- m_data_intranstivity_interaction_old <- rma.mv(d_calc ~ mean_age * intransitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_intran_old) -->
<!-- summary(m_data_intranstivity_interaction_old) -->
<!-- ``` -->

<!-- ### vocab  -->
<!-- ```{r plot_ITE_vocab} -->
<!-- m_data_intran_vocab %>%  -->
<!--   mutate(age_months = mean_age/30.44) %>%  -->
<!--   ggplot(aes(x = productive_vocab_median, y = d_calc, size = n_1, color = intransitive_event_type)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm") + -->
<!--   ylab("Effect Size") + -->
<!--   xlab("median vocab") + -->
<!--   ggtitle("Syntactical Bootstrapping effect size vs. median vocab, breakdown by intransitive_event_type")  -->
<!-- ``` -->

<!-- ```{r simple_model_ITE_vocab} -->
<!-- m_age_vs_intran_vocab <- rma.mv(d_calc ~ productive_vocab_median + intransitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_intran_vocab) -->

<!-- summary(m_age_vs_intran_vocab) -->
<!-- ``` -->

<!-- ```{r interaction_model_ITE_vocab} -->
<!-- m_data_intranstivity_interaction_vocab <- rma.mv(d_calc ~ productive_vocab_median * intransitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_intran_vocab) -->
<!-- summary(m_data_intranstivity_interaction_vocab) -->
<!-- ``` -->

<!-- ### vocab age comparsion  -->

<!-- ```{r plot_ITE_vocab_a} -->
<!-- m_data_intran_vocab %>%  -->
<!--   mutate(age_months = mean_age/30.44) %>%  -->
<!--   ggplot(aes(x = mean_age, y = d_calc, size = n_1, color = intransitive_event_type)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm") + -->
<!--   ylab("Effect Size") + -->
<!--   xlab("Age (months)") + -->
<!--   ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by intransitive_event_type")  -->
<!-- ``` -->

<!-- ```{r simple_model_ITE_vocab_a} -->
<!-- m_age_vs_intran_vocab <- rma.mv(d_calc ~ mean_age + intransitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_intran_vocab) -->

<!-- summary(m_age_vs_intran_vocab) -->
<!-- ``` -->

<!-- ```{r interaction_model_ITE_vocab_a} -->
<!-- m_data_intranstivity_interaction_vocab <- rma.mv(d_calc ~ mean_age * intransitive_event_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = m_data_intran_vocab) -->
<!-- summary(m_data_intranstivity_interaction_vocab) -->
<!-- ``` -->

## maybe need to look at the combination of transitive vs intransitive?
```{r}
ma_data %>% group_by(transitive_event_type, intransitive_event_type) %>% count()
```

## n_repetition_video (??) {.tabset}
```{r summary_plot_RV}
ma_data %>% ggplot(aes(x = n_repetitions_video)) +
  geom_histogram() 

```


# Testing Procedure 

## test_method (point vs look) (???) {.tabset}
```{r summary_TM}
ma_data %>% count(test_method)
```

## presentation_type (asynchronous vs immediate after )(maybe collapsing simultaneous with immediate after?) {.tabset}
```{r summary_and_seperate_PT}
ma_data %>% count(presentation_type)

ma_data_pt <- ma_data %>% 
  filter(presentation_type != "simultaneous") 

ma_data_pt_young <- ma_data_pt %>% 
  mutate(age_months = mean_age/30.44) %>% 
    filter(age_months < 36) 

ma_data_pt_old <- ma_data_pt %>% 
  mutate(age_months = mean_age/30.44) %>% 
    filter(age_months > 36 | age_months == 36) 

ma_data_pt_vocab <- ma_data_vocab %>% 
    filter(presentation_type != "simultaneous") 

  
```

### all
```{r plot_PT}
ma_data_pt %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1,  color = presentation_type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by presentation type") 
```

<!-- ```{r simple_PT} -->
<!-- m_age_pt <- rma.mv(d_calc ~ mean_age + presentation_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_pt) -->

<!-- summary(m_age_pt) -->
<!-- ``` -->

<!-- ```{r interaction_PT} -->
<!-- m_age_pt_interaction <- rma.mv(d_calc ~ mean_age * presentation_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_pt) -->
<!-- summary(m_age_pt_interaction) -->

<!-- ``` -->

<!-- ### <36, young -->
<!-- ```{r plot_PT_young} -->
<!-- ma_data_pt_young %>%  -->
<!--   mutate(age_months = mean_age/30.44) %>%  -->
<!--   ggplot(aes(x = age_months, y = d_calc, size = n_1,  color = presentation_type)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm") + -->
<!--   ylab("Effect Size") + -->
<!--   xlab("Age (months)") + -->
<!--   ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by presentation type, young only")  -->
<!-- ``` -->

<!-- ```{r simple_PT_young} -->
<!-- m_data_pt_young <- rma.mv(d_calc ~ mean_age + presentation_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_pt_young) -->


<!-- summary(m_age_pt) -->
<!-- ``` -->

<!-- ```{r interaction_PT_young} -->
<!-- m_age_pt_interaction_young <- rma.mv(d_calc ~ mean_age * presentation_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_pt_young) -->
<!-- summary(m_age_pt_interaction) -->
<!-- ``` -->

<!-- ### >= 36, old  -->
<!-- ```{r} -->
<!-- ma_data_pt_old %>%  -->
<!--   mutate(age_months = mean_age/30.44) %>%  -->
<!--   ggplot(aes(x = age_months, y = d_calc, size = n_1,  color = presentation_type)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm") + -->
<!--   ylab("Effect Size") + -->
<!--   xlab("Age (months)") + -->
<!--   ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by presentation type, young only")  -->
<!-- ``` -->

<!-- ### vocab  -->
<!-- ```{r plot_PT_vocab} -->
<!-- ma_data_pt_vocab %>%  -->
<!--   mutate(age_months = mean_age/30.44) %>%  -->
<!--   ggplot(aes(x = productive_vocab_median, y = d_calc, size = n_1,  color = presentation_type)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm") + -->
<!--   ylab("Effect Size") + -->
<!--   xlab("median vocab") + -->
<!--   ggtitle("Syntactical Bootstrapping effect size vs. median vocab, breakdown by presentation type")  -->
<!-- ``` -->

<!-- ```{r simple_PT_vocab} -->
<!-- m_pt_vocab <- rma.mv(d_calc ~ productive_vocab_median + presentation_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_pt_vocab) -->

<!-- summary(m_pt_vocab) -->
<!-- ``` -->

<!-- ```{r interaction_PT_vocab} -->
<!-- m_pt_vocab_interaction <- rma.mv(d_calc ~ productive_vocab_median * presentation_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_pt_vocab) -->
<!-- summary(m_pt_vocab_interaction) -->

<!-- ``` -->

<!-- ### vocab age comparsion  -->
<!-- ```{r plot_PT_vocab_a} -->
<!-- ma_data_pt_vocab %>%  -->
<!--   mutate(age_months = mean_age/30.44) %>%  -->
<!--   ggplot(aes(x = mean_age, y = d_calc, size = n_1,  color = presentation_type)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm") + -->
<!--   ylab("Effect Size") + -->
<!--   xlab("mean age ") + -->
<!--   ggtitle("Syntactical Bootstrapping effect size vs. mean age, breakdown by presentation type")  -->
<!-- ``` -->

<!-- ```{r simple_PT_vocab_a} -->
<!-- m_pt_vocab_a <- rma.mv(d_calc ~ mean_age + presentation_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_pt_vocab) -->

<!-- summary(m_pt_vocab_a) -->
<!-- ``` -->

<!-- ```{r interaction_PT_vocab_a} -->
<!-- m_pt_vocab_a_interaction <- rma.mv(d_calc ~ mean_age * presentation_type, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_pt_vocab) -->
<!-- summary(m_pt_vocab_a_interaction) -->

<!-- ``` -->

## character_identification {.tabset}
```{r count_ci}
ma_data %>% count(character_identification)
```

### all 
```{r plot_CI}
ma_data %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = character_identification)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by character_identification") 
```

```{r simple_CI}
m_age_ci <- rma.mv(d_calc ~ mean_age + character_identification, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)

summary(m_age_ci)
```

```{r interaction_CI}
m_age_stimuli_ci_interaction <- rma.mv(d_calc ~ mean_age * character_identification, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_stimuli_ci_interaction)
```


### <36, young

```{r plot_CI_young}
ma_data_young %>% 
  mutate(age_months = mean_age/30.44) %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = character_identification)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by character_identification, young only") 
```

```{r simple_CI_young}
m_age_ci_young <- rma.mv(d_calc ~ mean_age + character_identification, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)

summary(m_age_ci_young)
```

```{r interaction_CI_young}
m_age_ci_interaction_young <- rma.mv(d_calc ~ mean_age * character_identification, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
summary(m_age_ci_interaction_young)
```


### >= 36, old 
```{r plot_CI_old}
ma_data_old %>% 
  mutate(age_months = mean_age/30.44) %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = character_identification)) +
  geom_point() +
   geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by character_identification, old only") 
```

```{r simple_CI_old}
m_age_ci_old <- rma.mv(d_calc ~ mean_age + character_identification, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)

summary(m_age_ci_old)
```

```{r interaction_CI_old}
m_age_ci_interaction_old <- rma.mv(d_calc ~ mean_age * character_identification, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_old)
summary(m_age_ci_interaction_old)
```

### vocab 
```{r plot_CI_vocab}
ma_data_vocab %>% 
  mutate(age_months = mean_age/30.44) %>%
  ggplot(aes(x = productive_vocab_median, y = d_calc, size = n_1, color = character_identification)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("median vocab") +
  ggtitle("Syntactical Bootstrapping effect size vs. median voca, breakdown by character_identification, old only") 
```

<!-- ```{r simple_CI_vocab} -->
<!-- m_age_ci_vocab <- rma.mv(d_calc ~ productive_vocab_median + character_identification, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_vocab) -->

<!-- summary(m_age_ci_vocab) -->
<!-- ``` -->

<!-- ```{r interaction_CI_vocab} -->
<!-- m_age_ci_interaction_vocab <- rma.mv(d_calc ~ productive_vocab_median * character_identification, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_vocab) -->
<!-- summary(m_age_ci_interaction_vocab) -->
<!-- ``` -->

<!-- ### age w/ vocab comparison  -->
<!-- ```{r plot_CI_vocab_a} -->
<!-- ma_data_vocab %>%  -->
<!--   mutate(age_months = mean_age/30.44) %>% -->
<!--   ggplot(aes(x = mean_age, y = d_calc, size = n_1, color = character_identification)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm") + -->
<!--   ylab("Effect Size") + -->
<!--   xlab("Age (months)") + -->
<!--   ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by character_identification, old only")  -->
<!-- ``` -->

<!-- ```{r simple_CI_vocab_a} -->
<!-- m_age_ci_vocab_a <- rma.mv(d_calc ~ mean_age + character_identification, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_vocab) -->

<!-- summary(m_age_ci_vocab_a) -->
<!-- ``` -->

<!-- ```{r interaction_CI_vocab_a} -->
<!-- m_age_ci_interaction_vocab_a <- rma.mv(d_calc ~ mean_age * character_identification, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_vocab) -->
<!-- summary(m_age_ci_interaction_vocab_a) -->
<!-- ``` -->

## practice_phase {.tabset}

### all 
```{r plot_PP}
ma_data %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = practice_phase)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by practice_phase") 
```

```{r simple_PP}
m_age_pf <- rma.mv(d_calc ~ mean_age + character_identification, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)

summary(m_age_ci)
```

```{r interaction_PP}
m_age_pf_interaction <- rma.mv(d_calc ~ mean_age * character_identification, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_stimuli_ci_interaction)
```

### <36, young
```{r plot_PP_young}
ma_data_young %>% 
  mutate(age_months = mean_age/30.44) %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = practice_phase)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by practice_phase, young only") 
```

```{r simple_PP_young}
m_age_pf_young <- rma.mv(d_calc ~ mean_age + practice_phase, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)

summary(m_age_pf_young)
```

```{r interaction_PP_young}
m_age_pf_interaction_young <- rma.mv(d_calc ~ mean_age * practice_phase, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
summary(m_age_pf_interaction_young)
```

### >= 36, old 
```{r plot_PP_old}
ma_data_old %>% 
  mutate(age_months = mean_age/30.44) %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = practice_phase)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by practice_phase, old only") 
```

<!-- ```{r simple_PP_old} -->
<!-- m_age_pf_old <- rma.mv(d_calc ~ mean_age + practice_phase, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_old) -->

<!-- summary(m_age_pf_young) -->
<!-- ``` -->

<!-- ```{r interaction_PP_old} -->
<!-- m_age_pf_interaction_old <- rma.mv(d_calc ~ mean_age * practice_phase, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_old) -->
<!-- summary(m_age_pf_interaction_old) -->
<!-- ``` -->

### vocab
```{r plot_PP_vocab}
ma_data_vocab %>% 
  mutate(age_months = mean_age/30.44) %>%
  ggplot(aes(x = productive_vocab_median, y = d_calc, size = n_1, color = practice_phase)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("productive vocab") +
  ggtitle("Syntactical Bootstrapping effect size vs. productive vocab, breakdown by practice_phase, old only") 
```

```{r simple_PP_vcocab}
m_age_pf_vocab <- rma.mv(d_calc ~ productive_vocab_median + practice_phase, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab)

summary(m_age_pf_vocab)
```

```{r interaction_PP_vocab}
m_age_pf_interaction_vocab <- rma.mv(d_calc ~ productive_vocab_median * practice_phase, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab)
summary(m_age_pf_interaction_vocab)
```

### age w/ vocab comparsion 
```{r plot_PP_vocab_a}
ma_data_vocab %>% 
  mutate(age_months = mean_age/30.44) %>%
  ggplot(aes(x = mean_age, y = d_calc, size = n_1, color = practice_phase)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("mean age") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by practice_phase, old only") 
```

```{r simple_PP_vcocab_a}
m_age_pf_vocab_a <- rma.mv(d_calc ~ mean_age + practice_phase, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab)

summary(m_age_pf_vocab_a)
```

```{r interaction_PP_vocab_a}
m_age_pf_interaction_vocab_a <- rma.mv(d_calc ~ mean_age * practice_phase, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab)
summary(m_age_pf_interaction_vocab_a)
```

## test_mass_distributed {.tabset}
### all 
```{r plot_TT}
ma_data %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = test_mass_or_distributed)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by test type") 
```

```{r simple_TT}
m_age_tt <- rma.mv(d_calc ~ mean_age + test_mass_or_distributed, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)

summary(m_age_tt)
```

```{r interaction_TT}
m_age_tt_interaction <- rma.mv(d_calc ~ mean_age * test_mass_or_distributed, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_tt_interaction)
```

### <36, young
```{r plot_TT_young}
ma_data_young %>% 
  mutate(age_months = mean_age/30.44) %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = test_mass_or_distributed)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by test_mass_or_distributed, young only") 
```

```{r simple_TT_young}
m_age_tt_young <- rma.mv(d_calc ~ mean_age + test_mass_or_distributed, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)

summary(m_age_tt_young)
```

```{r interaction_TT_young}
m_age_tt_interaction_young <- rma.mv(d_calc ~ mean_age * test_mass_or_distributed, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young)
summary(m_age_tt_interaction_young)
```

### >= 36, old 
```{r plot_TT_old}
ma_data_old %>% 
  mutate(age_months = mean_age/30.44) %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1, color = test_mass_or_distributed)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by test_mass_or_distributed, old only") 
```

<!-- ```{r simple_TT_old} -->
<!-- m_age_tt_old <- rma.mv(d_calc ~ mean_age + test_mass_or_distributed, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_old) -->

<!-- summary(m_age_tt_old) -->
<!-- ``` -->

<!-- ```{r interaction_TT_old} -->
<!-- m_age_tt_interaction_old <- rma.mv(d_calc ~ mean_age * test_mass_or_distributed, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_old) -->
<!-- summary(m_age_tt_interaction_old) -->
<!-- ``` -->

### vocab 
```{r plot_TT_vocab}
ma_data_vocab %>% 
  mutate(age_months = mean_age/30.44) %>%
  ggplot(aes(x = productive_vocab_median, y = d_calc, size = n_1, color = test_mass_or_distributed)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("median vocab") +
  ggtitle("Syntactical Bootstrapping effect size vs. median voca, breakdown by test_mass_or_distributed, old only") 
```

<!-- ```{r simple_TT_vocab} -->
<!-- m_age_tt_vocab <- rma.mv(d_calc ~ productive_vocab_median + test_mass_or_distributed, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_vocab) -->

<!-- summary(m_age_tt_vocab) -->
<!-- ``` -->

<!-- ```{r interaction_TT_vocab} -->
<!-- m_age_tt_interaction_vocab <- rma.mv(d_calc ~ productive_vocab_median * test_mass_or_distributed, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_vocab) -->
<!-- summary(m_age_tt_interaction_vocab) -->
<!-- ``` -->

<!-- ### age w/ vocab comparison  -->
<!-- ```{r plot_TT_vocab_a} -->
<!-- ma_data_vocab %>%  -->
<!--   mutate(age_months = mean_age/30.44) %>% -->
<!--   ggplot(aes(x = mean_age, y = d_calc, size = n_1, color = test_mass_or_distributed)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm") + -->
<!--   ylab("Effect Size") + -->
<!--   xlab("Age (months)") + -->
<!--   ggtitle("Syntactical Bootstrapping effect size vs. Age (months), breakdown by test_mass_or_distributed, old only")  -->
<!-- ``` -->

<!-- ```{r simple_TT_vocab_a} -->
<!-- m_age_tt_vocab_a <- rma.mv(d_calc ~ mean_age + test_mass_or_distributed, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_vocab) -->

<!-- summary(m_age_tt_vocab_a) -->
<!-- ``` -->

<!-- ```{r interaction_TT_vocab_a} -->
<!-- m_age_tt_interaction_vocab_a <- rma.mv(d_calc ~ mean_age * test_mass_or_distributed, V = d_var_calc, -->
<!--                             random = ~ 1 | short_cite, data = ma_data_vocab) -->
<!-- summary(m_age_tt_interaction_vocab_a) -->
<!-- ``` -->


## n_train_test_pair (????){.tabset} 
```{r}
ma_data %>% ggplot(aes(x = n_train_test_pair)) +
  geom_histogram() 

```



## n_test_trial (???) {.tabset}
```{r}
ma_data %>% ggplot(aes(x = n_test_trial_per_pair)) +
  geom_histogram() 
```

