---
title: "Syntactic Boostrapping MA"
subtitle: "Data V2"
author: "Anjie Cao and Molly Lewis"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc_float: yes
    code_folding: hide 
    number_sections: no
    toc: yes
---


```{r setup, include = F}
library(tidyverse)
library(metafor)
library(knitr)
library(gridExtra)
library(here) # here package manages paths in a sane way
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.height=6, fig.path='Figs/',
                     warning=FALSE, message=FALSE)
theme_set(theme_classic()) # sets global plot theme
```



```{r}
DATA_PATH <- here("data/processed/syntactic_bootstrapping_tidy_data_molly.csv") 

ma_data <- read_csv(DATA_PATH) %>%
  mutate(row_id = 1:n()) %>%
  mutate(agent_argument_type2 = case_when(str_detect(agent_argument_type, "pronoun") ~ "pronoun",
                                          TRUE ~ "noun"),
         transitive_event_type2 = case_when(transitive_event_type == "direct_caused_action" ~ "direct_caused_action",
                                            TRUE ~ "indirect_caused_action"))
```

# Base model
```{r}
base_model <-  rma.mv(d_calc, d_var_calc, random = ~ 1 | short_cite/same_infant/row_id, data=ma_data)
base_model

forest(base_model)
funnel(base_model)
```

# Theoretical moderators

## Age
```{r}
age_model <-  rma.mv(d_calc ~ mean_age, d_var_calc, random = ~ 1 | short_cite/same_infant/row_id, data=ma_data)
age_model
age_model

ggplot(ma_data, aes(x = mean_age, y = d_calc)) +
  geom_point() +
  geom_smooth(method = "lm")
```


## Vocabulary

```{r}
vocab_model <-  rma.mv(d_calc ~ productive_vocab_median , d_var_calc, random = ~ 1 | short_cite/same_infant/row_id, data=ma_data)
vocab_model


```


## Sentence Structure
```{r}
structure_model <-  rma.mv(d_calc ~ sentence_structure, d_var_calc, random = ~ 1 | short_cite/same_infant/row_id, data=ma_data)
structure_model

```


## Agent argument type
```{r}
agent_argument_type_model <-  rma.mv(d_calc ~ agent_argument_type2, d_var_calc, random = ~ 1 | short_cite/same_infant/row_id, data=ma_data)
agent_argument_type_model

```

## Sink
```{r}
rma.mv(d_calc ~ agent_argument_type2 +sentence_structure + mean_age, d_var_calc, random = ~ 1 | short_cite/same_infant/row_id, data=ma_data)
```

## Transitive event type
```{r}
rma.mv(d_calc ~ transitive_event_type2, d_var_calc, random = ~ 1 | short_cite/same_infant/row_id, data=ma_data %>% filter(sentence_structure == "transitive"))
```

## Intransitive event type
```{r}
rma.mv(d_calc ~ intransitive_event_type , d_var_calc, random = ~ 1 | short_cite/same_infant/row_id, data=ma_data %>% filter(sentence_structure == "intransitive"))
```

## Methodological moderators

# Stimuli Modality
```{r}
rma.mv(d_calc ~ stimuli_modality, d_var_calc, random = ~ 1 | short_cite/same_infant/row_id, data=ma_data)
```

# Stimuli Actor
```{r}
rma.mv(d_calc ~ stimuli_actor, d_var_calc, random = ~ 1 | short_cite/same_infant/row_id, data=ma_data)
```

# Mass vs distributed
```{r}
rma.mv(d_calc ~ test_mass_or_distributed, d_var_calc, random = ~ 1 | short_cite/same_infant/row_id, data=ma_data)
```

# n_repetitions_sentence
Check this measure 
```{r}
rma.mv(d_calc ~ n_repetitions_sentence, d_var_calc, random = ~ 1 | short_cite/same_infant/row_id, data=ma_data)
```

# practice_phase
```{r}
rma.mv(d_calc ~ practice_phase, d_var_calc, random = ~ 1 | short_cite/same_infant/row_id, data=ma_data)
```

# character_identification
```{r}
rma.mv(d_calc ~ character_identification, d_var_calc, random = ~ 1 | short_cite/same_infant/row_id, data=ma_data)
```

# test_method
```{r}
rma.mv(d_calc ~ test_method, d_var_calc, random = ~ 1 | short_cite/same_infant/row_id, data=ma_data)
```


# Sink - choose moderators with model selcetion method?
```{r}
rma.mv(d_calc ~   test_mass_or_distributed   +
                  #practice_phase + 
                  character_identification + 
                  test_method +
                  stimuli_modality,
                  V = d_var_calc, 
       random = ~ 1 | short_cite/same_infant/row_id, data = ma_data)
```


# mega sink doesn't add much
```{r}
rma.mv(d_calc ~   test_mass_or_distributed   +
                  practice_phase + 
                  character_identification + 
                  test_method +
                  agent_argument_type2 +
                  sentence_structure + 
                  mean_age,
                  V = d_var_calc, 
       random = ~ 1 | short_cite/same_infant/row_id, data = ma_data)
```
