---
title: "Syntactic Boostrapping MA"
subtitle: "Data V2"
author: "Anjie Cao and Molly Lewis"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc_float: yes
    code_folding: hide 
    number_sections: no
    toc: yes
---


```{r setup, include = F}
library(tidyverse)
library(metafor)
library(knitr)
library(gridExtra)
library(here) # here package manages paths in a sane way
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.height=6, fig.path='Figs/',
                     warning=FALSE, message=FALSE)
theme_set(theme_classic()) # sets global plot theme
```



```{r}
DATA_PATH <- here("data/processed/syntactic_bootstrapping_tidy_data.csv") # make all variables (i.e. things that might change) as capital letters at the top of the scripts

ma_data <- read_csv(DATA_PATH)   %>%
  filter(language == "English",
         population_type == "typically_developing",
         stimuli_modality == "video",
         !is.na(mean_age)) 
  
```


# Data Overview

```{r}
#N_effect_sizes <- length((!is.na(ma_data$d_calc))&!(ma_data$d_calc ==0))
#N_papers <- length(unique(ma_data$unique_id))

# let's do this in the tidyverse way (which is much more readable)
n_effect_sizes <- ma_data %>%
  filter(!is.na(d_calc)) %>%
  nrow()

n_papers <- ma_data %>%
  distinct(unique_id) %>%
  nrow()
```

There are `r n_effect_sizes` effect sizes collected from `r n_papers` different papers.

Here are the papers in this analysis:

```{r}
ma_data %>%
  count(short_cite) %>%
  arrange(-n) %>%
  DT::datatable()
```


# Variable Summary 
## Continuous variables
```{r, fig.height =8 }
CONTINUOUS_VARS <- c("n_1", "x_1", "sd_1", "d_calc", "d_var_calc", "mean_age")

long_continuous <- ma_data %>%
  pivot_longer(cols = CONTINUOUS_VARS)

long_continuous %>%
  ggplot(aes(x = value)) +
  geom_histogram() + 
  facet_wrap(~ name, scale = "free_x") +
  labs(title = "Distribution of continuous measures")

long_continuous %>%
  group_by(name) %>%
  summarize(mean = mean(value),
            sd = sd(value)) %>%
  kable()

```  

## Categorical variables
```{r, fig.height = 10}
CATEGORICAL_VARS <- c("sentence_structure", "language", "population_type", 
                     "agent_argument_type", "patient_argument_type", "stimuli_type",
                     "stimuli_modality", "presentation_type", "character_identification",
                     "test_mass_or_distributed", "practice_phase")

long_categorical <- ma_data %>%
  pivot_longer(cols = CATEGORICAL_VARS) %>%
  count(name, value) # this is a short cut for group_by() %>% summarize(count = n()) 

long_categorical %>%
  ggplot(aes(x = value, y = n)) +  
  facet_wrap(~ name, scale = "free_x") +
  geom_col(position = 'dodge',width=0.4) + 
  theme(text = element_text(size=8),
        axis.text.x = element_text(angle = 90, hjust = 1))  # rotate x-axis text
```


# Explore Moderators

## no moderators{.tabset}

### all

```{r}
m1 <- rma.mv(d_calc, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m1)
```

### <36
```{r}
ma_data_young_only <- ma_data %>%
    mutate(age_months = mean_age/30.44) %>% 
    filter(age_months < 36) 

m_young <- rma.mv(d_calc, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young_only)
summary(m_young)
```


## Age only{.tabset}

### all
```{r}
ma_data %>% 
  ggplot(aes(x = mean_age/30.44, y = d_calc, size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_smooth(color = "red") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months)") +
  theme(legend.position = "none") 
```

```{r}
m_age <- rma.mv(d_calc ~ mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age)
```

### < 36
 
Let's only look at ES for kids < 36
```{r}
ma_data_young_only %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_smooth(color = "red") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days)") +
  theme(legend.position = "none") 
```

```{r}
m_age_young <- rma.mv(d_calc ~ mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young_only)
summary(m_age_young)
```


## age and sentence structure {.tabset}

### all
```{r}
ma_data %>% 
  filter(sentence_structure != "bare_verb") %>%
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1, , color = sentence_structure)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days)") 
```

```{r}
m_age_sentence <- rma.mv(d_calc ~ mean_age + sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_sentence)
```


Interaction:
```{r}
m_age_sentence <- rma.mv(d_calc ~ mean_age * sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_sentence)
```

### < 36 months
```{r}
ma_data_young_only <- ma_data %>%
    mutate(age_months = mean_age/30.44) %>% 
    filter(age_months < 36) 

ma_data_young_only %>% 
  filter(sentence_structure != "bare_verb") %>%
  ggplot(aes(x = age_months, y = d_calc, size = n_1, , color = sentence_structure)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days)") 
```

```{r}
m_age_sentence_young <- rma.mv(d_calc ~ mean_age + sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_young_only)
summary(m_age_sentence_young)
```

## Age and character identification

```{r}
ma_data %>% 
  ggplot(aes(x = mean_age, y = d_calc, color = character_identification)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  theme_classic() 
```

```{r}
m_age_char <- rma.mv(d_calc ~ mean_age + character_identification, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_char)
```

## Age and practice_phase
```{r}
ma_data %>% 
ggplot(aes(x = mean_age, y = d_calc, color = practice_phase)) +
  geom_point() +
  ylab("Effect Size") +
  geom_smooth(method = "lm") +
  xlab("Age (days)") +
  theme_classic()
```

```{r}
m_age_practice <- rma.mv(d_calc ~ mean_age + practice_phase, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_practice)
```

## Age and test_mass_or_distributed
```{r}
ma_data %>% 
  ggplot(aes(x = mean_age, y = d_calc, color = test_mass_or_distributed)) +
  geom_point() +
  ylab("Effect Size") +
  geom_smooth(method = "lm") +
  xlab("Age (days)") +
  theme_classic()
```

```{r}
m_age_test <- rma.mv(d_calc ~ mean_age + test_mass_or_distributed, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_test)
```


```{r}
m_age_test_int <- rma.mv(d_calc ~ mean_age * test_mass_or_distributed, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_test_int)
```


## Age and vocabulary
```{r}
ma_data_with_vocab <- ma_data %>% 
  mutate(vocab = case_when(!is.na(productive_vocab_median) ~ productive_vocab_median,
                           !is.na(productive_vocab_mean) ~ productive_vocab_mean,
                            TRUE ~ NA_real_),
         vocab_source = case_when(!is.na(productive_vocab_median) ~ "median",
                           !is.na(productive_vocab_mean) ~ "mean",
                            TRUE ~ NA_character_)) 
ma_data_with_vocab %>%
  ggplot(aes(x = mean_age, y = vocab, color = vocab_source)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic()

ma_data_with_vocab %>%
  ggplot(aes(x = productive_vocab_median, y = d_calc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_classic()
```

```{r}
cor.test(ma_data_with_vocab$mean_age,
         ma_data_with_vocab$productive_vocab_median)

m_age_vocab <- rma.mv(d_calc ~ productive_vocab_median + sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_vocab)

m_age_vocab_age <- rma.mv(d_calc ~ mean_age + sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data %>% filter(!is.na(productive_vocab_median)))
summary(m_age_vocab_age)
```


# Mega-model
```{r}
m_age_mega <- rma.mv(d_calc ~ mean_age + test_mass_or_distributed + practice_phase + character_identification + sentence_structure, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m_age_mega)
```

```
