---
title: "Verb_Extension_Explore"
author: "Anjie Cao and Molly Lewis"
date: "8/24/2020"
output: 
  html_document:
    toc_float: yes
    code_folding: hide 
    number_sections: no
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE, 
                      cache = FALSE,
                      #echo = FALSE,
                      fig.pos = "t!")
```

```{r cars}
library(papaja)
library(rmarkdown)
library(tidyverse) 
library(here)
library(glue)
library(metafor)
library(knitr)
library(gridExtra)
library(here)
library(heatmaply)
library(MuMIn)
library(glmulti)
library(PRISMAstatement)
library(PublicationBias)

DATA_PATH <- here("data/processed/verbextension_tidy_data.csv") 

ma_data <- read_csv(DATA_PATH) %>% mutate(row_id = 1:n())
ma_data_exclude_outlier <- read_csv(DATA_PATH) %>% mutate(row_id = 1:n()) %>% filter(plot_label != "Abbot-Smith, Imai, Durrant,& Nurmsoo (2017) - 2h") #%>% filter(plot_label != "Abbot-Smith, Imai, Durrant,& Nurmsoo (2017) - 2f")

```





# All Data

## Forest Plot 
```{r}

get_MA_params <- function(moderator, df) {
  
  this_data <- df
  n = nrow(this_data)
  
  if (moderator == TRUE){
      model <- rma.mv(d_calc ~ log(mean_age), V = d_var_calc,
                      random = ~ 1 | short_cite/same_infant/x_1,
                      method = "REML",
                      data = this_data)
      
      this_moderator_estimate <- model$b[2]
      this_moderator_estimate.cil <- model$ci.lb[2]
      this_moderator_estimate.cih <- model$ci.ub[2]
      this_moderator_z <- model$zval[2]
      this_moderator_p <- model$pval[2]

  } else{
      model <- rma.mv(d_calc, V = d_var_calc,
                      random = ~ 1 | short_cite/same_infant/x_1,
                      method = "REML",
                      data = this_data)
      
      this_moderator_estimate <- NA
      this_moderator_estimate.cil <- NA
      this_moderator_estimate.cih <- NA
      this_moderator_z <- NA
      this_moderator_p <- NA
    
  }
  
   params <- data.frame(this_moderator = moderator,
                       n = n,
                       estimate = model$b[1],
                       estimate.cil = model$ci.lb[1],
                       estimate.cih = model$ci.ub[1],
                       z = model$zval[1],
                       p = model$pval[1],
                       mod_estimate = this_moderator_estimate,
                       mod_estimate.cil = this_moderator_estimate.cil, 
                       mod_estimate.cih = this_moderator_estimate.cih,
                       moderator_z = this_moderator_z,
                       moderator_p = this_moderator_p,
                       Q = model$QE,
                       Qp = model$QEp)
  
  }

null_model<- get_MA_params(FALSE, ma_data)
#null_model
age_model <- get_MA_params(TRUE, ma_data)
all_models <- bind_rows(null_model,age_model)


mod_print <- all_models %>%
             mutate(esimate_print =  round(estimate, 2),
                    CI_print = paste0(" [", 
                                      round(estimate.cil, 2),
                                     ", ",
                                     round(estimate.cih, 2),
                                     "]"),
                   estimate_print_full = paste(esimate_print, CI_print),
                   z_print = round(z, 2),
                   p_print = round(p, 2),
                   p_print = ifelse(p_print <.001, "<.001", paste0("= ", p_print)),
                   mod_estimate_print = round(mod_estimate, 2),
                   mod_CI_print = paste0(" [", 
                                      round(mod_estimate.cil, 2),
                                     ", ",
                                     round(mod_estimate.cih, 2),
                                     "]"),
                   mod_estimate_print_full = paste(mod_estimate_print, mod_CI_print),

                   mod_z_print =  round(moderator_z, 2),
                   mod_p_print =  round(moderator_p, 2),
                   mod_p_print = ifelse(mod_p_print < .001, "<.001", 
                                        paste0("= ", mod_p_print)),
                   Q_print = round(Q, 2),
                   Qp_print = round(Qp, 2),
                   Qp_print = ifelse(Qp_print < .001, "<.001", paste0("= ", Qp_print)))
```

```{r fig.height = 22, fig.width = 20 }
alpha = 0.05
individual_data <- ma_data %>% 
  select(short_cite, unique_id,d_calc,d_var_calc, n_1, plot_label,sentence_structure) %>% 
  mutate(cil = d_calc - (qnorm(alpha / 2, lower.tail = FALSE) * sqrt(d_var_calc)),
         cil = case_when(
          (cil < -8) ~ -8,  # truncate error bar for visibility reason 
          TRUE ~ cil
         ),
         ciu = d_calc +
               qnorm(alpha / 2, lower.tail = FALSE) * sqrt(d_var_calc), 
         meta = "no", 
         label_color = "black",
         print_full = paste(round(d_calc,2), " [",round(cil,2),", ",round(ciu,2), "]", sep = "")
         )

cumulative <- mod_print %>% 
  filter(this_moderator == FALSE) %>% 
  select (estimate, estimate.cil, estimate.cih) %>% 
  mutate(short_cite = "Meta-Analytic Effect Size",
         plot_label = "Meta-Analytic Effect Size",
         d_calc = estimate, 
         d_var_calc = NA, 
         n_1 = 99, 
         expt_num = "", 
         expt_condition = "",
         cil = estimate.cil, 
         ciu = estimate.cih, 
         sentence_structure = "cumulative",
        print_full = paste(round(d_calc,2), " [",round(cil,2),", ",round(ciu,2), "]", sep = ""),
         meta = "yes", 
        label_color = "red")

forest_data <- bind_rows(individual_data, cumulative) 
forest_data$sentence_structure <- as.factor(forest_data$sentence_structure)
forest_data$meta <- as.factor(forest_data$meta)
forest_data <- forest_data %>% 
  rowid_to_column() %>% 
  mutate(
    rowid = if_else(rowid == 0, 99, as.double(rowid)) #to always put the MA ES at bottom
  ) %>% 
  group_by(sentence_structure) %>% arrange(-rowid, .by_group = TRUE)
forest_data$plot_label <- factor(forest_data$plot_label, levels = forest_data$plot_label)



# set the neighbourhood levels in the order the occur in the data frame
label_colors <- forest_data$label_color[order(forest_data$plot_label)]

forest_data %>%  # First sort by val. This sort the dataframe but NOT the factor levels
  ggplot(aes(x = plot_label, y = d_calc)) + 
  geom_point(data = forest_data,
             aes(size=n_1, shape = sentence_structure, color = sentence_structure)) + 
  scale_color_manual(breaks = c("cumulative", "intransitive","transitive"),
                     values = c("red", "black", "black"))+ 
  scale_size(guide = 'none') + 
  scale_shape_manual(breaks = c("cumulative", "intransitive","transitive"),
                     values=c(18,16, 17)) +
  #guides(color = guide_legend(override.aes = list(shape = 18, shape = 16, shape = 17))) + 
  geom_linerange(aes(ymin = cil, ymax = ciu, color = sentence_structure), show.legend = FALSE) + 
  geom_segment(aes(x = plot_label, y = d_calc, xend = plot_label, yend = cil),
               linejoin = "round", 
               lineend = "round", 
               size = 0.1,
               arrow = arrow(length = unit(0.1, "inches")),
               data = filter(forest_data,cil == -8))+
  geom_hline(aes(yintercept = 0),  color = "gray44",linetype = 2) + 
  geom_hline(aes(yintercept = filter(forest_data, sentence_structure == "cumulative")$d_calc), 
             color = "red", linetype = 2) + 
  geom_text(aes(label = print_full, x = plot_label, y = 7), 
            size = 3.5, colour = label_colors) + 
  scale_y_continuous(breaks = seq(-10, 5, 1))+ 
  coord_cartesian(clip = 'on') + 
  coord_flip() + 
  ylab("Cohen's d") +
  labs(color  = "Effect Size Type",shape = "Effect Size Type") + # merge two legends 
  theme(text = element_text(size=18),
        legend.position="bottom",   
        plot.margin = unit(c(1,2,16,1), "lines"),
        legend.title = element_blank(),
        panel.background = element_blank(),
       #panel.background = element_rect(fill = "white", colour = "grey50"),
        axis.title.y = element_blank(),
        axis.text.y = element_text(colour = label_colors)) 
```



## Regression Test 
### Funnel Plot 
```{r}
base_model_no_mv <-  rma(d_calc,  d_var_calc, data=ma_data)
funnel(base_model_no_mv)
```

### Base Model Regression Test 
```{r}
base_model_no_mv <-  rma(d_calc,  d_var_calc, data=ma_data)
regtest(base_model_no_mv, predictor = 'sei', ret.fit = T)
```

### Multi-level Model Regression Test 
```{r}
rma.mv(d_calc ~ sqrt(d_var_calc),  d_var_calc,  
                         random = ~ 1 | short_cite/same_infant/row_id, data=ma_data)
```



## PublicationBias Package  
### P-val Plot 
```{r}
pval_plot(ma_data$d_calc,
ma_data$d_var_calc, alpha.select = 0.05) 
```
### Eta analysis {.tabset}

#### eta curve
```{r}
eta <- data.frame()

for (i in 1:20){
  df <- corrected_meta(
      ma_data$d_calc,
      ma_data$d_var_calc,
      eta= i,
      clustervar = 1:length(ma_data$d_calc),
      model = "robust",
      selection.tails = 1, # if changed to 2, the curve is flat
      favor.positive = TRUE,# if changed to False, the curve is flat
      alpha.select = 0.05,
      CI.level = 0.95,
      small = TRUE)
  eta <- bind_rows(eta, df)
  
}
eta %>% ggplot(aes(x = eta, y = pval)) + 
  geom_point() + 
  geom_line() + 
  geom_hline(yintercept = 0.05, color = "red", type = 2) + 
  labs(title = "eta vs pval")
```
#### plot 

```{r}
eta.list = as.list( c( 200, 150, 100, 50, 40, 30, 20, rev( seq(1,15,1) ) ) )
res.list = lapply(eta.list, function(x){
cat("\n Working on eta = ", x)
return(corrected_meta(
      ma_data$d_calc,
      ma_data$d_var_calc,
      eta= x,
      clustervar = 1:length(ma_data$d_calc),
      model = "robust",
      selection.tails = 1,
      favor.positive = TRUE,
      alpha.select = 0.05,
      CI.level = 0.95,
      small = TRUE) )
})


res.df = as.data.frame(do.call("rbind",res.list)) 

ggplot( data = res.df, aes( x = eta, y = est ) ) +
geom_ribbon( data = res.df, aes( x = eta, ymin = lo, ymax = hi ), fill = "gray" ) +
geom_line( lwd = 1.2 ) +
xlab( bquote( eta ) ) +
ylab( bquote( hat(mu)[eta] ) ) +
theme_classic()
```

### significance_funnel
```{r}
significance_funnel(
ma_data$d_calc,
ma_data$d_var_calc,
xmin = min(ma_data$d_calc),
xmax = max(ma_data$d_calc),
ymin = 0,
ymax = max(sqrt(ma_data$d_var_calc)),
xlab = "Point estimate",
ylab = "Estimated standard error",
favor.positive = TRUE,
est.all = NA,
est.N = NA,
alpha.select = 0.05,
plot.pooled = TRUE
)
```

### Estimate the S_val
```{r}
sval <- data.frame()

for (i in seq(0, 0.1, by = 0.02)){
  s <- svalue(
          ma_data$d_calc,
          ma_data$d_var_calc,
          q = i,
          clustervar = 1:length(ma_data$d_calc),
          model = "robust",
          alpha.select = 0.05,
          eta.grid.hi = 200,
          favor.positive = TRUE,
          CI.level = 0.95,
          small = TRUE,
          return.worst.meta = FALSE
          )
  s <- s %>% mutate(q_val = i)

  sval <- bind_rows(sval, s) 
}

sval
```

## null and age model 
```{r}
null <- rma.mv(d_calc, V = d_var_calc,
                      random = ~ 1 | short_cite/same_infant/row_id,
                      method = "REML",
                      data = ma_data)
age <- rma.mv(d_calc ~ mean_age, V = d_var_calc,
                      random = ~ 1 | short_cite/same_infant/row_id,
                      method = "REML",
                      data = ma_data)
age

ma_data %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Verb Extension effect size vs. Age (months)") 
```



# Excluding Outlier 
```{r}
overall_mean <- mean(ma_data$d_calc)
overall_sd <- sd(ma_data$d_calc)

ma_data %>% 
  filter(d_calc > overall_mean + (2*(overall_sd)) | d_calc < overall_mean - (2*(overall_sd)) ) %>% 
  select(plot_label)
```

## No outlier Forest Plot 
```{r}

get_MA_params <- function(moderator, df) {
  
  this_data <- df
  n = nrow(this_data)
  
  if (moderator == TRUE){
      model <- rma.mv(d_calc ~ log(mean_age), V = d_var_calc,
                      random = ~ 1 | short_cite/same_infant/x_1,
                      method = "REML",
                      data = this_data)
      
      this_moderator_estimate <- model$b[2]
      this_moderator_estimate.cil <- model$ci.lb[2]
      this_moderator_estimate.cih <- model$ci.ub[2]
      this_moderator_z <- model$zval[2]
      this_moderator_p <- model$pval[2]

  } else{
      model <- rma.mv(d_calc, V = d_var_calc,
                      random = ~ 1 | short_cite/same_infant/x_1,
                      method = "REML",
                      data = this_data)
      
      this_moderator_estimate <- NA
      this_moderator_estimate.cil <- NA
      this_moderator_estimate.cih <- NA
      this_moderator_z <- NA
      this_moderator_p <- NA
    
  }
  
   params <- data.frame(this_moderator = moderator,
                       n = n,
                       estimate = model$b[1],
                       estimate.cil = model$ci.lb[1],
                       estimate.cih = model$ci.ub[1],
                       z = model$zval[1],
                       p = model$pval[1],
                       mod_estimate = this_moderator_estimate,
                       mod_estimate.cil = this_moderator_estimate.cil, 
                       mod_estimate.cih = this_moderator_estimate.cih,
                       moderator_z = this_moderator_z,
                       moderator_p = this_moderator_p,
                       Q = model$QE,
                       Qp = model$QEp)
  
  }

null_model<- get_MA_params(FALSE, ma_data_exclude_outlier)
#null_model
age_model <- get_MA_params(TRUE, ma_data_exclude_outlier)
all_models <- bind_rows(null_model,age_model)


mod_print <- all_models %>%
             mutate(esimate_print =  round(estimate, 2),
                    CI_print = paste0(" [", 
                                      round(estimate.cil, 2),
                                     ", ",
                                     round(estimate.cih, 2),
                                     "]"),
                   estimate_print_full = paste(esimate_print, CI_print),
                   z_print = round(z, 2),
                   p_print = round(p, 2),
                   p_print = ifelse(p_print <.001, "<.001", paste0("= ", p_print)),
                   mod_estimate_print = round(mod_estimate, 2),
                   mod_CI_print = paste0(" [", 
                                      round(mod_estimate.cil, 2),
                                     ", ",
                                     round(mod_estimate.cih, 2),
                                     "]"),
                   mod_estimate_print_full = paste(mod_estimate_print, mod_CI_print),

                   mod_z_print =  round(moderator_z, 2),
                   mod_p_print =  round(moderator_p, 2),
                   mod_p_print = ifelse(mod_p_print < .001, "<.001", 
                                        paste0("= ", mod_p_print)),
                   Q_print = round(Q, 2),
                   Qp_print = round(Qp, 2),
                   Qp_print = ifelse(Qp_print < .001, "<.001", paste0("= ", Qp_print)))
```

```{r fig.height = 22, fig.width = 20 }
alpha = 0.05
individual_data <- ma_data_exclude_outlier %>% 
  select(short_cite, unique_id,d_calc,d_var_calc, n_1, plot_label,sentence_structure) %>% 
  mutate(cil = d_calc - (qnorm(alpha / 2, lower.tail = FALSE) * sqrt(d_var_calc)),
         cil = case_when(
          (cil < -8) ~ -8,  # truncate error bar for visibility reason 
          TRUE ~ cil
         ),
         ciu = d_calc +
               qnorm(alpha / 2, lower.tail = FALSE) * sqrt(d_var_calc), 
         meta = "no", 
         label_color = "black",
         print_full = paste(round(d_calc,2), " [",round(cil,2),", ",round(ciu,2), "]", sep = "")
         )

cumulative <- mod_print %>% 
  filter(this_moderator == FALSE) %>% 
  select (estimate, estimate.cil, estimate.cih) %>% 
  mutate(short_cite = "Meta-Analytic Effect Size",
         plot_label = "Meta-Analytic Effect Size",
         d_calc = estimate, 
         d_var_calc = NA, 
         n_1 = 99, 
         expt_num = "", 
         expt_condition = "",
         cil = estimate.cil, 
         ciu = estimate.cih, 
         sentence_structure = "cumulative",
        print_full = paste(round(d_calc,2), " [",round(cil,2),", ",round(ciu,2), "]", sep = ""),
         meta = "yes", 
        label_color = "red")

forest_data <- bind_rows(individual_data, cumulative) 
forest_data$sentence_structure <- as.factor(forest_data$sentence_structure)
forest_data$meta <- as.factor(forest_data$meta)
forest_data <- forest_data %>% 
  rowid_to_column() %>% 
  mutate(
    rowid = if_else(rowid == 0, 99, as.double(rowid)) #to always put the MA ES at bottom
  ) %>% 
  group_by(sentence_structure) %>% arrange(-rowid, .by_group = TRUE)
forest_data$plot_label <- factor(forest_data$plot_label, levels = forest_data$plot_label)



# set the neighbourhood levels in the order the occur in the data frame
label_colors <- forest_data$label_color[order(forest_data$plot_label)]

forest_data %>%  # First sort by val. This sort the dataframe but NOT the factor levels
  ggplot(aes(x = plot_label, y = d_calc)) + 
  geom_point(data = forest_data,
             aes(size=n_1, shape = sentence_structure, color = sentence_structure)) + 
  scale_color_manual(breaks = c("cumulative", "intransitive","transitive"),
                     values = c("red", "black", "black"))+ 
  scale_size(guide = 'none') + 
  scale_shape_manual(breaks = c("cumulative", "intransitive","transitive"),
                     values=c(18,16, 17)) +
  #guides(color = guide_legend(override.aes = list(shape = 18, shape = 16, shape = 17))) + 
  geom_linerange(aes(ymin = cil, ymax = ciu, color = sentence_structure), show.legend = FALSE) + 
  geom_segment(aes(x = plot_label, y = d_calc, xend = plot_label, yend = cil),
               linejoin = "round", 
               lineend = "round", 
               size = 0.1,
               arrow = arrow(length = unit(0.1, "inches")),
               data = filter(forest_data,cil == -8))+
  geom_hline(aes(yintercept = 0),  color = "gray44",linetype = 2) + 
  geom_hline(aes(yintercept = filter(forest_data, sentence_structure == "cumulative")$d_calc), 
             color = "red", linetype = 2) + 
  geom_text(aes(label = print_full, x = plot_label, y = 7), 
            size = 3.5, colour = label_colors) + 
  scale_y_continuous(breaks = seq(-10, 5, 1))+ 
  coord_cartesian(clip = 'on') + 
  coord_flip() + 
  ylab("Cohen's d") +
  labs(color  = "Effect Size Type",shape = "Effect Size Type") + # merge two legends 
  theme(text = element_text(size=18),
        legend.position="bottom",   
        plot.margin = unit(c(1,2,16,1), "lines"),
        legend.title = element_blank(),
        panel.background = element_blank(),
       #panel.background = element_rect(fill = "white", colour = "grey50"),
        axis.title.y = element_blank(),
        axis.text.y = element_text(colour = label_colors)) 
```


## No outlier Regression Test 
### Funnel Plot No outlier
```{r}
base_model <-  rma(d_calc,  d_var_calc,  
                         data=ma_data_exclude_outlier)

funnel(base_model)
```

### No outlier Base Model Reg test 
```{r}
regtest(base_model, predictor = 'sei', ret.fit = T)
```


### No outlier Multi-level Model Regression Test
```{r}
rma.mv(d_calc ~ sqrt(d_var_calc),  d_var_calc,  
                         random = ~ 1 | short_cite/same_infant/row_id, data=ma_data_exclude_outlier)
```
### No outlier Multi-level Model Regression Test with Age 
```{r}
rma.mv(d_calc ~ sqrt(d_var_calc) + mean_age,  d_var_calc,  
                         random = ~ 1 | short_cite/same_infant/row_id, data=ma_data_exclude_outlier)
```




## No outlier PublicationBias Package  
### No outlier P-val Plot 
```{r}
pval_plot(ma_data_exclude_outlier$d_calc,
ma_data$d_var_calc, alpha.select = 0.05) 
```
### Eta analysis {.tabset}

#### eta curve
```{r}
eta <- data.frame()

for (i in 1:20){
  df <- corrected_meta(
      ma_data_exclude_outlier$d_calc,
      ma_data_exclude_outlier$d_var_calc,
      eta= i,
      clustervar = 1:length(ma_data_exclude_outlier$d_calc),
      model = "robust",
      selection.tails = 1, # if changed to 2, the curve is flat
      favor.positive = TRUE,# if changed to False, the curve is flat
      alpha.select = 0.05,
      CI.level = 0.95,
      small = TRUE)
  eta <- bind_rows(eta, df)
  
}
eta %>% ggplot(aes(x = eta, y = pval)) + 
  geom_point() + 
  geom_line() + 
  geom_hline(yintercept = 0.05, color = "red", type = 2) + 
  labs(title = "eta vs pval")
```
#### plot 

```{r}
eta.list = as.list( c( 200, 150, 100, 50, 40, 30, 20, rev( seq(1,15,1) ) ) )
res.list = lapply(eta.list, function(x){
cat("\n Working on eta = ", x)
return(corrected_meta(
      ma_data_exclude_outlier$d_calc,
      ma_data_exclude_outlier$d_var_calc,
      eta= x,
      clustervar = 1:length(ma_data_exclude_outlier$d_calc),
      model = "robust",
      selection.tails = 1,
      favor.positive = TRUE,
      alpha.select = 0.05,
      CI.level = 0.95,
      small = TRUE) )
})


res.df = as.data.frame(do.call("rbind",res.list)) 

ggplot( data = res.df, aes( x = eta, y = est ) ) +
geom_ribbon( data = res.df, aes( x = eta, ymin = lo, ymax = hi ), fill = "gray" ) +
geom_line( lwd = 1.2 ) +
xlab( bquote( eta ) ) +
ylab( bquote( hat(mu)[eta] ) ) +
theme_classic()
```

### significance_funnel
```{r}
significance_funnel(
ma_data_exclude_outlier$d_calc,
ma_data_exclude_outlier$d_var_calc,
xmin = min(ma_data_exclude_outlier$d_calc),
xmax = max(ma_data_exclude_outlier$d_calc),
ymin = 0,
ymax = max(sqrt(ma_data_exclude_outlier$d_var_calc)),
xlab = "Point estimate",
ylab = "Estimated standard error",
favor.positive = TRUE,
est.all = NA,
est.N = NA,
alpha.select = 0.05,
plot.pooled = TRUE
)
```

### Estimate the S_val
```{r}
sval <- data.frame()

for (i in seq(0, 0.1, by = 0.02)){
  s <- svalue(
          ma_data_exclude_outlier$d_calc,
          ma_data_exclude_outlier$d_var_calc,
          q = i,
          clustervar = 1:length(ma_data_exclude_outlier$d_calc),
          model = "robust",
          alpha.select = 0.05,
          eta.grid.hi = 200,
          favor.positive = TRUE,
          CI.level = 0.95,
          small = TRUE,
          return.worst.meta = FALSE
          )
  s <- s %>% mutate(q_val = i)

  sval <- bind_rows(sval, s) 
}

sval
```



## Null and age model 
```{r}
null <- rma.mv(d_calc, V = d_var_calc,
                      random = ~ 1 | short_cite/same_infant/row_id,
                      method = "REML",
                      data = ma_data_exclude_outlier)
age <- rma.mv(d_calc ~ mean_age, V = d_var_calc,
                      random = ~ 1 | short_cite/same_infant/row_id,
                      method = "REML",
                      data = ma_data_exclude_outlier)
age

ma_data_exclude_outlier %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Verb Extension effect size vs. Age (months)") 
```

# explore stimuli contrast
```{r}

sc <- rma.mv(d_calc ~ stimuli_contrast, V = d_var_calc,
                      random = ~ 1 | short_cite/same_infant/row_id,
                      method = "REML",
                      data = ma_data_exclude_outlier)

sc

ma_data_exclude_outlier %>% 
  mutate(age_months = mean_age/30.44) %>% 
  ggplot(aes(x = age_months, y = d_calc, color = stimuli_contrast)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Verb Extension effect size vs. Age (months)") 
```
```{r}
ma_data_object_change <- ma_data %>% 
                           filter(stimuli_contrast == "object_change") 

oc_only <- rma.mv(d_calc, V = d_var_calc,
                      random = ~ 1 | short_cite/same_infant/row_id,
                      method = "REML",
                      data = ma_data_object_change)

oc_age <- rma.mv(d_calc ~ mean_age, V = d_var_calc,
                      random = ~ 1 | short_cite/same_infant/row_id,
                      method = "REML",
                      data = ma_data_object_change)

summary(oc_only)
summary(oc_age)
```

## reg test with object_change, null model  
publication bias yes: 
```{r}
rma.mv(d_calc ~ sqrt(d_var_calc),  d_var_calc,  
                         random = ~ 1 | short_cite/same_infant/row_id, data=ma_data_object_change)
```
## reg test with object_change, with age 

```{r}
rma.mv(d_calc ~ sqrt(d_var_calc) + mean_age,  d_var_calc,  
                         random = ~ 1 | short_cite/same_infant/row_id, data=ma_data_object_change)
```
