

```{r, eval = F}


transitive <- rma.mv(d_calc ~ 1, 
                  V = d_var_calc,
                  random = ~ 1 | short_cite/same_infant/row_id,
                  method = "REML",
                  data = filter(ma_data, sentence_structure == "transitive"))


transitive

intransitive <- rma.mv(d_calc ~ 1, 
                  V = d_var_calc,
                  random = ~ 1 | short_cite/same_infant/row_id,
                  method = "REML",
                  data = filter(ma_data, sentence_structure == "intransitive"))
intransitive
```



Three decades of research on syntactic bootstrapping has extended our understanding of early verb acquisition. Here we built upon these previous studies by presenting a quantitative synthesis of the literature using meta-analytic methods. We find a small effect of syntactic bootstrapping, comparable in size to that of sound-symbolism and cross-situational learning.  We then used the meta-analytic method to examine how the strength of the syntactic bootstrapping effect varies as a function of developmental change and syntactic structure.  We find no evidence that the strength of the syntactic bootstrapping effect changes across development. In contrast, we find some evidence that the strength of the effect is influenced by predicate type: the syntactic bootstrapping effect is present for transitive sentences, but not intransitive sentences. We also examined a range of methodological features and found no evidence that the size of the effect was influenced.


Importantly, we also find evidence for some publication bias in the syntactic bootstrapping literature in two different analyses. This suggests that there may be several “missing”, null or negative studies in our meta-analysis, potentially leading to an overestimation of the overall effect size.  While this finding suggests that estimates of the magnitude of the effect should be interpreted with caution, there is no reason to think that publication bias interacts with the moderators of interest. 


## Small effect size
Even in the presence of publication bias, the syntactic bootstrapping effect (d = `r filter(mod_print, moderator == "NULL")$estimate_print`) is small by conventional Cohen's d standards (CITATION??),  and also small relative to other early word learning biases and strategies typically studied with nouns, like mutual exclusivity and gaze-following. On the one hand, this small effect size is consonant with the fact that verbs tend to be learned later in development than nouns: If verb learning strategies are weaker than those for nouns, we would expect verbs to be learned later. On the other hand, children do eventually develop a large vocabulary of verbs, despite no developmental change in the strength of the syntactic bootstrapping effect.  This raises an important puzzle: if syntactic bootstrapping does not play a prominent role in helping children learn verbs, then how do children learn them? 

One possibility is that children learn verbs using many of the same strategies typically thought of as noun-learning strategies. Indeed, while word learning is typically studied with nouns, there is some evidence that a wide range of word learning strategies may be helpful in verb learning, beyond syntactic bootstrapping. Mutual exclusivity [@merriman1993four; @golinkoff1996lexical; @merriman1996young], cross situational learning [@scott20122; @monaghan2015gavagai], sound symbolism [@kantartzis2011japanese; @imai2008sound] and the use of social cues [@tomasello1994learning; @roseberry2009live] has all been studied under verb learning contexts. Each of these strategies and bias has been found to facilitate the mapping between verbs and actions. Of course, these possible learning strategies are not mutually exclusive to one another, including syntactic bootstrapping. In actual learning situations, children are most likely to be using a combination of the strategies. Future research is needed to answer how these learning strategies emerge throughout development and help children better learn verbs. 


## Lack of age effect
Notably, we do not find the syntactic bootstrapping effect gets larger with age. This finding is consistent with the proposal that syntactic bootstrapping is an unlearned bias [@fisher2020developmental; @gleitman1990structural], and therefore the accumulation of experience should not have a significant impact on this effect as children grow older. However, an unlearned bias does not necessarily imply that the effect sizes should remain unchanged. Older children with larger vocabulary sizes are more likely to be familiar with the linguistic input containing novel verbs. They are also better learners with faster information processing capacity and longer attention span. An alternative explanation for the lack of developmental change is the methodological adaptations.There is reason to think that researchers adapt to the stimuli and the testing procedures to children’s age [@bergmann2018promoting]. These more challenging paradigms bring up the task demand and “cancel” the growing capabilities children possess. Nevertheless, there are reasons to believe the methodological adaptation is not primarily responsible for the lack of age effect in the syntactic bootstrapping study. We examined numerous methodological moderators and none of them significantly change the age model’s results. Furthermore, we also visually inspect the change in visual stimuli use as a function of age (See SI, Sec.X). The only notable difference in the visual complexity of the stimuli is the contrast between the stimuli used by @jin2015role for 15-month-olds and the remaining ones, so the visual complexity by itself can not explain the lack of age effect in the current study. 

```{r}
summarise_age <- ma_data %>% summarise(
  min_age = round(min(mean_age_months), 0), 
  max_age = round(max(mean_age_months), 0)
)

```


A final possibility is that there is developmental change in the size of the effect, but this change is not detected in the current meta-analysis.It is possible that syntactic bootstrapping’s developmental change happens in a later age than the age range included in the current samples. There is evidence that young children would experience a “relational shift”, that is, a period of time that they gradually shift their attention from objects to the relations between objects [@gentner1988metaphor; @gentner1991language]. Considering that both verbs and grammatical constructions are relational categories [@gentner2006verbs; @goldwater2017grammatical], it is possible that the developmental change would only emerge as children experience the “relational shift”. Moreover, children at different ages weight cues differently. It has been demonstrated that when both syntactic cues and socio-pragmatic cues are present, five-years-old children prioritize the former over the latter more than three-years-old children [@nappa2009use]. Therefore, children included in the current samples with age ranging from `r summarise_age$min_age` months to `r summarise_age$max_age` months old may show limited developmental change in their abilities to use syntactic bootstrapping as a verb learning strategy. In addition, a possibility that we can not rule out is that the developmental change is present but small, and our sample size has insufficient power to detect it. 

## Transitivity effect 

Our meta-analysis revealed that the syntactic bootstrapping effect is only observed with certain kinds of syntactic structures:  children only learn verbs in conditions using transitive sentences, but not in conditions using intransitive sentences. This finding is consistent with the observations many researchers have made [@yuan2012counting; @arunachalam2010meaning]. Three factors may have given rise to this transitivity advantage. First, under certain contexts, the transitive sentences have less ambiguity than their intransitive counterparts.  If one sees two scenes: in one a girl patting a boy, in the other a girl and a boy jumping side-by-side, then upon hearing “the girl is gorping the boy”, only the scene with patting action is a plausible interpretation. In contrast, if one hears the intransitive sentence, “the girl is gorping”,  the verb can be interpreted as being consistent with both the causative scene and the non-causative scene. Second, children may have more experience with transitive sentences than intransitive sentences. A corpus analysis on parental utterances for 1- to 6-year-old children found that transitive sentences make up approximately 24.36% of all utterances, whereas intransitive sentences occupy only 17.24% [@laakso2007pronouns]. Thus the familiarity with transitive sentences can potentially improve children’s understanding of transitive sentences in the lab. Last but not least, the perceptual saliency of the visual scenes may have contributed to the asymmetrical performance in the transitive conditions and the transitive conditions. Children were found to have a baseline preference for two actors events over one actor event [e.g., @yuan2012counting], and for synchronous movement over causative movement [e.g., @naigles1993first]. These preferences can make detecting an effect in the transitive condition easier than in the intransitive condition. 

The lack of effect in intransitive sentences also opens up the question on the generalizability of syntactic bootstrapping effect: what other syntactic structures can syntactic bootstrapping be extended to? Can it be applied to the learning of adjectives and adverbs, which are two syntactic categories similarly abstract like verbs? Alternatively, is syntactic bootstrapping only plausible in transitive sentences? If that is the case, then what features of transitive sentences make them uniquely conducive to verb learning? 


## Limitations and recommendations for future works 

```{r}
sample_summary <- ma_data %>% summarise(
  mean = round(mean(n_1),1), 
  sd = round(sd(n_1), 1)
)
```


Like any method, meta-analysis has a number of limitations.  Most notably, the meta-analytic method is influenced by publication bias in the literature it draws upon. Although our sensitivity analysis suggests that the effect size can not be reduced to zero even after assuming the “worst-case scenario”, it still weakens the evidential value of the current literature and makes the small effect size difficult to interpret. We make two recommendations based on this finding. First, we noticed that the studies included in the current meta-analysis tend to have a small sample size (Mean = `r sample_summary$mean`; SD = `r sample_summary$sd`, see SI sec. 8) and therefore suffer from low power. While the current metaanalysis increased the power by aggregating across the studies, the findings are potentially compromised by publication bias. We recommend future researchers to conduct a preregistered direct replication with large sample sizes. Based on the existing effect sizes, we ran a power-analysis using the pwr package’s one-sample proportion test (cite metalab? Cite package?), and we found that in order to reach 0.8 power for the main effect the sample size needs to be about 104 participants.  We recognize the practical challenges associated with recruiting a large number of infant participants, and thus our second recommendation for the field is to consider pre-registered large-scale multi-lab collaborations [e.g. @manybabies2020quantifying]. These collaborations can provide high-powered insights into understanding the phenomena, and also serve as a valuable opportunity to address a second limitation of the current meta-analysis: the homogeneity of the sample. 

A second limitation is the narrow scope of participants in our meta-analysis: English-speaking, typically developing children. The homogeneity of the samples included prevents us from understanding the generalizability of syntactic bootstrapping in a broader sense. For example, English primarily uses word order as syntactic markers. The positions in which the verbs occur in the sentences are relatively stable. One question can not be answered with the homogeneous sample is whether children whose first language does not mark syntactic categories with word orders would use syntactic bootstrapping as well. Including more diverse samples in the meta-analysis can enable us to understand how the linguistics features moderate the syntactic bootstrapping effect. We want to highlight that there are a growing number of studies that investigate syntactic bootstrapping in other languages [e.g. Mandarin: @lee2008mandarin; Korean: @jin2015role; Turkish: @goksun2008turkish] as well as children with developmental disorders [e.g. Children with ASD: @naigles2011abstractness; Children with Down syndrom: @grela2002lexical; Children with Specific Language Impairment: @o1997syntactic]. We decided to not include these studies due to their slightly different methodologies and insufficient sample sizes to generate meaningful comparisons. Nevertheless, we will be updating our dataset and adding more moderators on Metalab, so in the future, the community will be able to explore the effect of language and developmental disorders on syntactic bootstrapping. 

## Conclusion
In sum, syntactic bootstrapping is one of the leading proposals for how children learn verbs -- an increasingly large part of children’s vocabulary. Our meta-analysis suggests that while syntactic bootstrapping may be one route to early verb learning, it is a small effect relative to other word learning strategies and may not be robust to a wide range of syntactic structures. Our work highlights the need for pre-registered, high-powered replications of the syntactic bootstrapping effect, and future research examining how syntactic bootstrapping interacts with other word learning strategies.  


