---
title: "Syntactic Bootstrapping Publication Bias"
author: "Anjie Cao and Molly Lewis"
date: "8/24/2020"
output: 
  html_document:
    toc_float: yes
    code_folding: hide 
    number_sections: no
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE, 
                      cache = FALSE,
                      #echo = FALSE,
                      fig.pos = "t!")
library(rmarkdown)
library(tidyverse) 
library(here)
library(metafor)
library(knitr)
library(here)
library(PublicationBias)
```

```{r}
DATA_PATH <- here("data/processed/syntactic_bootstrapping_tidy_data.csv") 
ma_data <- read.csv(DATA_PATH) %>%  mutate(row_id = 1:n())
```

# Forest Plot 
There are `r ma_data %>% count()` effect sizes from `r ma_data %>% select(unique_id) %>% unique() %>% count()` unique papers. 

```{r}

get_MA_params <- function(moderator, df) {
  
  this_data <- df
  n = nrow(this_data)
  
  if (moderator == TRUE){
      model <- rma.mv(d_calc ~ log(mean_age), V = d_var_calc,
                      random = ~ 1 | short_cite/same_infant/x_1,
                      method = "REML",
                      data = this_data)
      
      this_moderator_estimate <- model$b[2]
      this_moderator_estimate.cil <- model$ci.lb[2]
      this_moderator_estimate.cih <- model$ci.ub[2]
      this_moderator_z <- model$zval[2]
      this_moderator_p <- model$pval[2]

  } else{
      model <- rma.mv(d_calc, V = d_var_calc,
                      random = ~ 1 | short_cite/same_infant/x_1,
                      method = "REML",
                      data = this_data)
      
      this_moderator_estimate <- NA
      this_moderator_estimate.cil <- NA
      this_moderator_estimate.cih <- NA
      this_moderator_z <- NA
      this_moderator_p <- NA
    
  }
  
   params <- data.frame(this_moderator = moderator,
                       n = n,
                       estimate = model$b[1],
                       estimate.cil = model$ci.lb[1],
                       estimate.cih = model$ci.ub[1],
                       z = model$zval[1],
                       p = model$pval[1],
                       mod_estimate = this_moderator_estimate,
                       mod_estimate.cil = this_moderator_estimate.cil, 
                       mod_estimate.cih = this_moderator_estimate.cih,
                       moderator_z = this_moderator_z,
                       moderator_p = this_moderator_p,
                       Q = model$QE,
                       Qp = model$QEp)
  
  }

null_model<- get_MA_params(FALSE, ma_data)
#null_model
age_model <- get_MA_params(TRUE, ma_data)
all_models <- bind_rows(null_model,age_model)


mod_print <- all_models %>%
             mutate(esimate_print =  round(estimate, 2),
                    CI_print = paste0(" [", 
                                      round(estimate.cil, 2),
                                     ", ",
                                     round(estimate.cih, 2),
                                     "]"),
                   estimate_print_full = paste(esimate_print, CI_print),
                   z_print = round(z, 2),
                   p_print = round(p, 2),
                   p_print = ifelse(p_print <.001, "<.001", paste0("= ", p_print)),
                   mod_estimate_print = round(mod_estimate, 2),
                   mod_CI_print = paste0(" [", 
                                      round(mod_estimate.cil, 2),
                                     ", ",
                                     round(mod_estimate.cih, 2),
                                     "]"),
                   mod_estimate_print_full = paste(mod_estimate_print, mod_CI_print),

                   mod_z_print =  round(moderator_z, 2),
                   mod_p_print =  round(moderator_p, 2),
                   mod_p_print = ifelse(mod_p_print < .001, "<.001", 
                                        paste0("= ", mod_p_print)),
                   Q_print = round(Q, 2),
                   Qp_print = round(Qp, 2),
                   Qp_print = ifelse(Qp_print < .001, "<.001", paste0("= ", Qp_print)))
```

```{r fig.height = 22, fig.width = 20 }
alpha = 0.05
individual_data <- ma_data %>% 
  select(short_cite, unique_id,d_calc,d_var_calc, n_1, plot_label,sentence_structure) %>% 
  mutate(cil = d_calc - (qnorm(alpha / 2, lower.tail = FALSE) * sqrt(d_var_calc)),
         cil = case_when(
          (cil < -8) ~ -8,  # truncate error bar for visibility reason 
          TRUE ~ cil
         ),
         ciu = d_calc +
               qnorm(alpha / 2, lower.tail = FALSE) * sqrt(d_var_calc), 
         meta = "no", 
         label_color = "black",
         print_full = paste(round(d_calc,2), " [",round(cil,2),", ",round(ciu,2), "]", sep = "")
         )

cumulative <- mod_print %>% 
  filter(this_moderator == FALSE) %>% 
  select (estimate, estimate.cil, estimate.cih) %>% 
  mutate(short_cite = "Meta-Analytic Effect Size",
         plot_label = "Meta-Analytic Effect Size",
         d_calc = estimate, 
         d_var_calc = NA, 
         n_1 = 99, 
         expt_num = "", 
         expt_condition = "",
         cil = estimate.cil, 
         ciu = estimate.cih, 
         sentence_structure = "cumulative",
        print_full = paste(round(d_calc,2), " [",round(cil,2),", ",round(ciu,2), "]", sep = ""),
         meta = "yes", 
        label_color = "red")

forest_data <- bind_rows(individual_data, cumulative) 
forest_data$sentence_structure <- as.factor(forest_data$sentence_structure)
forest_data$meta <- as.factor(forest_data$meta)
forest_data <- forest_data %>% 
  rowid_to_column() %>% 
  mutate(
    rowid = if_else(rowid == 0, 99, as.double(rowid)) #to always put the MA ES at bottom
  ) %>% 
  group_by(sentence_structure) %>% arrange(-rowid, .by_group = TRUE)
forest_data$plot_label <- factor(forest_data$plot_label, levels = forest_data$plot_label)



# set the neighbourhood levels in the order the occur in the data frame
label_colors <- forest_data$label_color[order(forest_data$plot_label)]

forest_data %>%  # First sort by val. This sort the dataframe but NOT the factor levels
  ggplot(aes(x = plot_label, y = d_calc)) + 
  geom_point(data = forest_data,
             aes(size=n_1, shape = sentence_structure, color = sentence_structure)) + 
  scale_color_manual(breaks = c("cumulative", "intransitive","transitive"),
                     values = c("red", "black", "black"))+ 
  scale_size(guide = 'none') + 
  scale_shape_manual(breaks = c("cumulative", "intransitive","transitive"),
                     values=c(18,16, 17)) +
  #guides(color = guide_legend(override.aes = list(shape = 18, shape = 16, shape = 17))) + 
  geom_linerange(aes(ymin = cil, ymax = ciu, color = sentence_structure), show.legend = FALSE) + 
  geom_segment(aes(x = plot_label, y = d_calc, xend = plot_label, yend = cil),
               linejoin = "round", 
               lineend = "round", 
               size = 0.1,
               arrow = arrow(length = unit(0.1, "inches")),
               data = filter(forest_data,cil == -8))+
  geom_hline(aes(yintercept = 0),  color = "gray44",linetype = 2) + 
  geom_hline(aes(yintercept = filter(forest_data, sentence_structure == "cumulative")$d_calc), 
             color = "red", linetype = 2) + 
  geom_text(aes(label = print_full, x = plot_label, y = 7), 
            size = 3.5, colour = label_colors) + 
  scale_y_continuous(breaks = seq(-10, 5, 1))+ 
  coord_cartesian(clip = 'on') + 
  coord_flip() + 
  ylab("Cohen's d") +
  labs(color  = "Effect Size Type",shape = "Effect Size Type") + # merge two legends 
  theme(text = element_text(size=18),
        legend.position="bottom",   
        plot.margin = unit(c(1,2,16,1), "lines"),
        legend.title = element_blank(),
        panel.background = element_blank(),
       #panel.background = element_rect(fill = "white", colour = "grey50"),
        axis.title.y = element_blank(),
        axis.text.y = element_text(colour = label_colors)) 
```

Mixed effect model:
```{r}
base_model_mv <-  rma.mv(d_calc,  d_var_calc,  
                         random = ~ 1 | short_cite/same_infant/row_id, data=ma_data)

base_model_mv
```


# Funnel Plot with no moderators
```{r}
funnel(base_model_mv)
```


### Egger's Test 
Significantly asymmetrical, by Egger's test.
```{r}
rma.mv(d_calc ~ sqrt(d_var_calc),  d_var_calc,  
                         random = ~ 1 | short_cite/same_infant/row_id, data=ma_data)
```



# Sensitivity Analysis (Mathur & VanderWeele, 2020)
## P-val plot 
Checking the assumption that publication bias favors positive results only. This plot provides some evidence that studies favor “significant” results regardless of the sign. Is this enough to violate the model assumption?
```{r}
pval_plot(ma_data$d_calc,
ma_data$d_var_calc, alpha.select = 0.05) 
```

## Estimate true eta

```{r}
get_corrected_ma <- function(args, df){
  args <- unlist(args)

    cluster_val = df$unique_id
   if(args[2] == "independent"){
      cluster_val = 1:nrow(df)
   } else {
      cluster_val = df$unique_id
   }
  
  corrected_meta(
      df$d_calc,
      df$d_var_calc,
      eta = as.numeric(args[1]),
      clustervar = cluster_val,
      model = "robust",
      selection.tails = as.numeric(args[3]), 
      favor.positive = TRUE,
      small = TRUE) %>%
    mutate(eta = as.numeric(args[1]),
           clustered = args[2],
           selection_tails = as.numeric(args[3]))
}

eta_estimates <- list(c(200, 150, 100, 50, 40, 30, 20, rev(seq(1,15,1))),
     c("independent", "clustered"),
     c(1,2)) %>%
  cross() %>%
  map_df(get_corrected_ma, ma_data) %>%
  mutate(selection_tails = fct_recode(as.factor(selection_tails),
                                      "one_sided" = "1",
                                      "two_sided" = "2"))

ggplot(eta_estimates, aes(x = eta, y = est)) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "gray" ) +
    geom_line(aes(color = clustered), size = 1.2) +
    geom_hline(aes(yintercept = 0), linetype = 2) +
    facet_grid(clustered ~ selection_tails) +
    xlab(bquote(eta)) +
    ylab(bquote(hat(mu)[eta])) +
    theme_classic() +
    theme(legend.position = "none")
```

Not sure why clustered doesn't differ more from non-clustered?

## Eta estimate under worst case publication bias scenario

Calculate worst case point estimate:

(non-affirmative studies only; corresponds to grey diamond in plot )
```{r}
ma_data_with_affirm <- ma_data %>%
  mutate(pvalue =  2 * (1 - pnorm( abs(d_calc / sqrt(d_var_calc)))),
         affirm =  (d_calc > 0) & (pvalue < 0.05))

affirm_model<- rma.mv(d_calc,  d_var_calc,  
                         random = ~ 1 | short_cite/same_infant/row_id, data=
          ma_data_with_affirm %>% filter(affirm == FALSE)) 

affirm_estimate <- as.numeric(affirm_model$b)
 
all_model <- rma.mv(d_calc,  d_var_calc,  
                         random = ~ 1 | short_cite/same_infant/row_id, data=
          ma_data_with_affirm)
all_estimate <- as.numeric(all_model$b)

```


```{r}
m = significance_funnel(
  ma_data$d_calc,
  ma_data$d_var_calc,
  xmin = min(ma_data$d_calc),
  xmax = max(ma_data$d_calc),
  ymin = 0,
  ymax = max(sqrt(ma_data$d_var_calc)),
  xlab = "Point estimate",
  ylab = "Estimated standard error",
  favor.positive = TRUE,
  est.all = all_estimate,
  est.N = affirm_estimate,
  alpha.select = 0.05,
  plot.pooled = TRUE
)

m
```


Estimate S val (critical value of eta; publication bias) to attenunate mu to critical value (q). This plot shows that no value of eta could attenuate the point estimate to 0. But not much publication bias would attenuate the CI to include 0. 

S (t, q) as the value of η that would attenuate t to q, where q < t (where t in meta-anayltic estimate).
 
svalest = eta to attentuate point estimate to 0; sval.ci = eta to attentunate ci to 0.  
```{r}
get_s_value <- function(i, df){

 svalue(df$d_calc,
        df$d_var_calc,
        q = i,
        clustervar = df$unique_id,
        model = "robust",
        alpha.select = 0.05,
        eta.grid.hi = 200,
        favor.positive = TRUE,
      #  CI.level = 0.95,
        small = TRUE) %>%
    mutate(q = i,
           sval.est = as.numeric(as.character(sval.est)),
           sval.ci = as.numeric(as.character(sval.ci)))  # necessary for binding rows
}

s_values <- seq(0,0, 0) %>%
  map_df(get_s_value, ma_data) 

ggplot(s_values, aes(x = q, y = sval.est)) +
  geom_point() +
  geom_line() +
  theme_classic()

kable(s_values)
```
