---
title: "model plot"
author: "anjie"
date: "9/20/2020"
output: 
  html_document:
    number_sections: no
    toc_float: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rmarkdown)
library(tidyverse) 
library(here)
library(metafor)
library(knitr)
library(janitor)
library(insight)

source(here("writeups/paper/scripts/model_print.R"))
DATA_PATH <- here("data/processed/syntactic_bootstrapping_tidy_data.csv") 


```

# Get single predictor model 
```{r}
ma_data <- read_csv(DATA_PATH)
MODERATORS <- c( "NULL", "mean_age","productive_vocab_median", "sentence_structure", "agent_argument_type", "patient_argument_type","agent_argument_number", "n_repetitions_sentence", "n_repetitions_video", "stimuli_modality", "stimuli_actor", "transitive_event_type","intransitive_event_type", "visual_stimuli_pair", "test_method","presentation_type","character_identification", "practice_phase", "test_mass_or_distributed", "n_train_test_pair", "n_test_trial_per_pair", "presentation_type_collapsed")
mod_print <- generate_moderator_df(MODERATORS, ma_data)


```
## for theoretical moderators 
```{r message=FALSE}
THEORETICAL_MODERATORS <- c("mean_age", "sentence_structure", "agent_argument_type")

theoretical_df <- mod_print %>%
  filter(this_moderator %in% THEORETICAL_MODERATORS) %>% 
  select(this_moderator, mod_estimate, mod_estimate.cih, mod_estimate.cil) %>% 
  mutate(model = "single", 
         type = "theoretical")


```

## for methodological moderators 
```{r message=FALSE}
METHODOLOGICAL_MODERATORS <- c("character_identification", "practice_phase", "test_mass_or_distributed","n_repetitions_sentence", "presentation_type_collapsed") 

methodological_df <-  mod_print %>%
  filter(this_moderator %in% METHODOLOGICAL_MODERATORS) %>% 
  select(this_moderator, mod_estimate, mod_estimate.cih, mod_estimate.cil) %>% 
  mutate(model = "single", 
         type = "methodological")



methodological_df <-  mod_print %>%
  filter(this_moderator %in% METHODOLOGICAL_MODERATORS) %>% 
  select(this_moderator, mod_estimate, mod_estimate.cih, mod_estimate.cil) %>% 
  mutate(model = "single", 
         type = "methodological") 
```


# Get mega model info
## for theoretical moderators
```{r message=FALSE}
theoretical_mod <- rma.mv(d_calc ~ sentence_structure + agent_argument_type + mean_age, V = d_var_calc,
                    random = ~ 1 | short_cite/same_infant/x_1,
                     method = "REML",
                     data = ma_data) 

theoretical_mod_print <- generate_mega_model_df(theoretical_mod)

theoretical_mega_df <- theoretical_mod_print %>% 
  filter(moderator_name != "intrcpt") %>% 
  mutate(
    this_moderator = case_when(
      moderator_name == "sentence_structuretransitive" ~ "sentence_structure", 
      moderator_name == "agent_argument_typepronoun" ~ "agent_argument_type", 
      TRUE ~ moderator_name
    ),
    mod_estimate.cih = model_ci_ub, 
    mod_estimate.cil = model_ci_lb
  )  %>% 
  select(this_moderator, mod_estimate, mod_estimate.cih, mod_estimate.cil) %>% 
  mutate(model = "full", 
          type = "theoretical")

```

## for methodological moderators
```{r message=FALSE}

methodological_mod <- rma.mv(d_calc ~ character_identification + practice_phase + presentation_type_collapsed + test_mass_or_distributed + n_repetitions_sentence,
                             V = d_var_calc,
                    random = ~ 1 | short_cite/same_infant/x_1,
                     method = "REML",
                     data = ma_data)



methodological_mod_print <- generate_mega_model_df(methodological_mod)

methodological_mega_df <- methodological_mod_print %>% 
  filter(moderator_name != "intrcpt") %>% 
  mutate(
    this_moderator = case_when(
      moderator_name == "character_identificationyes" ~ "character_identification", 
      moderator_name == "practice_phaseyes" ~ "practice_phase",
      moderator_name == "test_mass_or_distributedmass" ~ "test_mass_or_distributed",
      moderator_name == "presentation_type_collapsedsimultaneous" ~ "presentation_type_collapsed",
      TRUE ~ moderator_name
    ),
    mod_estimate.cih = model_ci_ub, 
    mod_estimate.cil = model_ci_lb
  )  %>% 
  select(this_moderator, mod_estimate, mod_estimate.cih, mod_estimate.cil) %>% 
  mutate(model = "full", 
         type = "methodological")
```

# Combine df 

```{r message=FALSE}
methodological_all_df <- bind_rows(methodological_df, methodological_mega_df)
theoretical_all_df <- bind_rows(theoretical_df, theoretical_mega_df)
```

# Generate plot for theoretical moderators 

```{r}
t_df <- theoretical_all_df %>%
  mutate(
    this_moderator = case_when(
      this_moderator == "mean_age" ~ "Mean Age", 
      this_moderator == "agent_argument_type" ~ "Agent Argument Type", 
      this_moderator == "sentence_structure" ~ "Sentence Structure"
    )
  ) 

m_df <- methodological_all_df %>% 
  mutate( this_moderator = case_when(
    this_moderator == "practice_phase" ~ "Practice Phase", 
    this_moderator == "n_repetitions_sentence" ~ "Sentence Repetitions", 
    this_moderator == "character_identification" ~ "Character Identification Phase", 
    this_moderator == "presentation_type_collapsed" ~ "Synchronicity", 
    this_moderator == "test_mass_or_distributed" ~ "Testing Procedure Structure", 
  ))

all_df <- bind_rows(t_df, m_df)
all_df
```



```{r message=FALSE}
SEED = 1
Jitter = 0.1  



t_df %>% 
  ggplot(aes(x = fct_reorder(this_moderator, -mod_estimate), color = model, 
             y = mod_estimate, 
             ymin = mod_estimate.cil, 
             ymax = mod_estimate.cih, 
             group = model)) + 
  geom_pointrange(size = 1, position = position_dodge(0.5)) + 
  scale_color_manual(values = c("grey", "red")) + 
  geom_line(#data = theoretical_all_df %>% filter(model == "full"), 
            aes(x = fct_reorder(this_moderator, -mod_estimate),
                y = mod_estimate, 
                group = model,
                color = model),
            position = position_dodge(0.5),
            alpha = 0.5, 
            #color = "grey", 
            size = 0.5) + 
  geom_hline(yintercept = 0, color = "black", linetype="dashed")+
  coord_flip() + 
  theme(
        axis.line = element_line(size = 1.2),
        axis.ticks = element_line(size = 1),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank()) + 
  xlab("") + 
  ylab("Estimate") 
  
```

# Generate plot for methodological moderators 

```{r message=FALSE}
m_df %>% 
    ggplot(aes(x = fct_reorder(this_moderator, -mod_estimate), color = model, 
             y = mod_estimate, 
             ymin = mod_estimate.cil, 
             ymax = mod_estimate.cih, 
             group = model)) + 
  geom_pointrange(size = 1, position = position_dodge(0.5)) + 
  scale_color_manual(values = c("grey", "red")) + 
  geom_line(#data = theoretical_all_df %>% filter(model == "full"), 
            aes(x = fct_reorder(this_moderator, -mod_estimate),
                y = mod_estimate, 
                group = model,
                color = model),
            position = position_dodge(0.5),
            alpha = 0.5, 
            #color = "grey", 
            size = 0.5) + 
  geom_hline(yintercept = 0, color = "black", linetype="dashed")+
  coord_flip() + 
  theme(
        axis.line = element_line(size = 1.2),
        axis.ticks = element_line(size = 1),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank()) + 
  xlab("") + 
  ylab("Estimate")
```

# plot predicted values  
```{r}
vocab_model <- rma.mv(d_calc ~ productive_vocab_median, V = d_var_calc,
                    random = ~ 1 | short_cite/same_infant/x_1,
                     method = "REML",
                     data = ma_data) 

age_model <- rma.mv(d_calc ~ mean_age, V = d_var_calc,
                    random = ~ 1 | short_cite/same_infant/x_1,
                     method = "REML",
                     data = ma_data) 



predicted_val_vocab <- predict(vocab_model, addx = TRUE) %>% 
  as.data.frame() %>% 
  rownames_to_column("data_frame_id") %>%
  select(data_frame_id, pred) %>%
  left_join(ma_data %>% rownames_to_column("data_frame_id") %>%
              select(productive_vocab_median, d_calc, data_frame_id)) %>%
  mutate(model_type = "vocab") %>%
  rename(developmental_predictor = productive_vocab_median)

predicted_val_age <- predict(age_model, addx = TRUE) %>% 
  as.data.frame() %>% 
  rownames_to_column("data_frame_id") %>%
  select(data_frame_id, pred) %>%
  left_join(ma_data %>% rownames_to_column("data_frame_id") %>%
              select(mean_age, d_calc, data_frame_id)) %>%
  mutate(model_type = "age") %>%
  rename(developmental_predictor = mean_age)

bind_rows(predicted_val_vocab, predicted_val_age) %>%
  ggplot() +
  geom_point(aes(x = developmental_predictor, y = d_calc)) +
  geom_smooth(method = "lm",
              aes(x = developmental_predictor, y = pred), se = T) +
  facet_wrap(~ model_type, scales = "free_x") +
  theme_bw()


bind_rows(predicted_val_vocab, predicted_val_age) %>%
  ggplot(aes(x = developmental_predictor, y = d_calc)) +
  geom_smooth(method = "lm") +
  facet_wrap(~ model_type, scales = "free_x") +
  theme_bw()



bind_rows(predicted_val_vocab, predicted_val_age) %>%
  ggplot() +
  geom_point(aes(x = developmental_predictor, y = d_calc))+
  geom_smooth(method = "lm",
              aes(x = developmental_predictor, y = pred)) +
    geom_smooth(method = "lm",
              aes(x = developmental_predictor, y = d_calc), color = "red") +
  facet_wrap(~ model_type, scales = "free_x") +
  theme_bw()





```

```{r}
predicted_val_vocab %>% 
  ggplot(aes(x = productive_vocab_median, y = predicted_value)) + 
  geom_point()
```

## weird looking predicted values when using two moderators plot 
```{r}
predicted_val_both %>% 
  ggplot(aes(x = productive_vocab_median, y = predicted_value)) + 
  geom_point()
```



```{r}
ma_data %>% 
  ggplot(aes(x = productive_vocab_median, y = d_calc)) + 
  geom_point() + 
  geom_line(
    data = predicted_val_vocab, 
    aes(x = productive_vocab_median, y = predicted_value)) + 
  geom_line(
    data = predicted_val_both, 
    aes(x = productive_vocab_median, y = predicted_value)) # werid looking line comes from the two predictors model 


```

# what's wrong with funnel plot? 
Is there a difference between two types of funnel plot? 
Fancier: 
```{r}
mixed_model <- rma.mv(d_calc ~ 1,  d_var_calc,  
                   random = ~ 1 | short_cite/same_infant/x_1, 
                   method = "REML", 
                   data=ma_data)
funnel(mixed_model)
```
basic: 
```{r}
basic_model <- rma(d_calc ~ 1,  d_var_calc,  
                   data=ma_data)
funnel(basic_model)
```
ok they defintiely look too similar, excerpt from r documents: 

> For fixed- and random-effects models (i.e., models not involving moderators), the plot shows the individual observed effect sizes or outcomes on the x-axis against the corresponding standard errors (i.e., the square root of the sampling variances) on the y-axis.

so maybe they are the same? Is there a way to take into account the random effects in the funnel? the `predict` function does give me what is needed: 
```{r}
predict(mixed_model)
```



