---
title: "sb DRAFT-high confidence"
output:
  html_document:
    df_print: paged
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                     warning=FALSE, message=FALSE)
```



```{r}
library(tidyverse)
library(googlesheets4)
library(metafor)
library(knitr)
library(gridExtra)
source("calculate_es_bootstrapping.R")
source("tidy_data_bootstrapping.R")
GOOGLE_SHEET_ID <- "1kSL5lpmHcaw9lOp2dhJ_RH15REFe7oZVwMO1vJc930o"
```



```{r}

read_raw_data_and_clean("1kSL5lpmHcaw9lOp2dhJ_RH15REFe7oZVwMO1vJc930o")
write_tidy_sheet("1kSL5lpmHcaw9lOp2dhJ_RH15REFe7oZVwMO1vJc930o")
ma_data <- read_sheet(MA_DATA_GOOGLE_SHEET_ID, "MA data tidy with ES NEW")


ma_data <- ma_data %>% filter(!is.na(d_calc)) %>% mutate(practice_phase = ifelse(practice_phase == "NA","no",practice_phase),
                                                         character_identification = ifelse(character_identification == "NA", "no", character_identification),
                                                         presentation_type = ifelse(presentation_type == "immediate-after", "immediate_after", ifelse(presentation_type == "Immediate-after", "immediate_after", presentation_type)),
                                                         patient_argument_type = ifelse(patient_argument_type == "N/A", "NA", patient_argument_type),
                                                         population_type = ifelse(population_type == "typical_developing", "typically_developing", population_type),
                                                         agent_argument_type = ifelse(agent_argument_type == "pronoun_and_noun" | agent_argument_type == "pronoung_and_noun", "noun_and_pronoun", agent_argument_type),
                                                         test_type = ifelse(test_type == "actor", "agent", test_type))
ma_data %>% filter(inclusion_certainty == 2)-> ma_data
```


# Data Overview

- number of differnet effectsizes
- number of conditions included 

```{r}
N_effect_sizes <- length((!is.na(ma_data$d_calc))&!(ma_data$d_calc ==0))
N_papers <- length(unique(ma_data$unique_id))
```

There are `r N_effect_sizes` effect sizes collected from `r N_papers` different papers.



# Variable Summary 
- distribution of sample size 
```{r}

summary(ma_data$n_1)
ma_data %>% 
  ggplot(aes(x = n_1)) + 
  geom_histogram() + 
  geom_vline(xintercept =mean(ma_data$n_1)) +
  stat_bin(binwidth = 2) + 
  labs(title = "Distribution of sample size")


```

- distribtuion of x_1 
```{r}

summary(ma_data$x_1)
ma_data %>% 
  ggplot(aes(x = x_1)) + 
  geom_histogram() + 
  stat_bin(binwidth = 0.05) + 
  geom_vline(xintercept =mean(ma_data$x_1))+
  labs(title = "Distribution of x_1")

```
- distribtuion of sd_1 

```{r}
summary(ma_data$SD_1)
ma_data %>% 
  ggplot(aes(x =SD_1 )) + 
  geom_histogram() + 
  stat_bin(binwidth = 0.01) + 
  geom_vline(xintercept =mean(ma_data$SD_1))+
  labs(title = "Distribution of sd_1")
```

- distribution of d_calc
```{r}
summary(ma_data$d_calc)
ma_data %>% 
  ggplot(aes(x =d_calc )) + 
  geom_histogram() + 
  geom_vline(xintercept = mean(ma_data$d_calc))+
  labs(title = "Distribution of d_calc")
```

- summary for all categorical variables 

```{r}
ma_data %>% group_by(sentence_structure) %>% 
  summarize(count = n()) %>% ggplot(aes(x=sentence_structure, y=count)) +     
  geom_col(position = 'dodge',width=0.4) + 
  theme(text = element_text(size=8)) ->p1

ma_data %>% group_by(language) %>% 
  summarize(count = n()) %>% ggplot(aes(x=language, y=count)) +     
  geom_col(position = 'dodge',width=0.4) + 
  theme(text = element_text(size=8)) ->p2

ma_data %>% group_by(population_type) %>% 
  summarize(count = n()) %>% ggplot(aes(x=population_type, y=count)) +     
  geom_col(position = 'dodge',width=0.4) + 
  theme(text = element_text(size=8))->p3

ma_data %>% group_by(agent_argument_type) %>% 
  summarize(count = n()) %>% ggplot(aes(x=agent_argument_type, y=count)) +     
  geom_col(position = 'dodge',width=0.4) + 
  theme(text = element_text(size=8))->p4

ma_data %>% group_by(patient_argument_type) %>% 
  summarize(count = n()) %>% ggplot(aes(x=patient_argument_type	, y=count)) +     
  geom_col(position = 'dodge',width=0.4) + 
  theme(text = element_text(size=8))->p5

ma_data %>% group_by(stimuli_type) %>% 
  summarize(count = n()) %>% ggplot(aes(x=stimuli_type	, y=count)) +     
  geom_col(position = 'dodge',width=0.4) + 
  theme(text = element_text(size=8))->p6

ma_data %>% group_by(stimuli_modality) %>% 
  summarize(count = n()) %>% ggplot(aes(x=stimuli_modality, y=count)) +     
  geom_col(position = 'dodge',width=0.4) + 
  theme(text = element_text(size=8))->p7

ma_data %>% group_by(stimuli_actor) %>% 
  summarize(count = n()) %>% ggplot(aes(x=stimuli_actor, y=count)) +     
  geom_col(position = 'dodge',width=0.4) + 
  theme(text = element_text(size=8))->p8

ma_data %>% group_by(presentation_type) %>% 
  summarize(count = n()) %>% ggplot(aes(x=presentation_type, y=count)) +     
  geom_col(position = 'dodge',width=0.4) + 
  theme(text = element_text(size=8))->p9

ma_data %>% group_by(character_identification) %>% 
  summarize(count = n()) %>% ggplot(aes(x=character_identification, y=count)) +     
  geom_col(position = 'dodge',width=0.4) + 
  theme(text = element_text(size=8))->p10

ma_data %>% group_by(practice_phase) %>% 
  summarize(count = n()) %>% ggplot(aes(x=practice_phase, y=count)) +     
  geom_col(position = 'dodge',width=0.4) + 
  theme(text = element_text(size=8))->p11

ma_data %>% group_by(test_mass_or_distributed) %>% 
  summarize(count = n()) %>% ggplot(aes(x=test_mass_or_distributed, y=count)) +     
  geom_col(position = 'dodge',width=0.4) + 
  theme(text = element_text(size=8))->p12

margin = theme(plot.margin = unit(c(2,2,2,2), "cm"))
grid.arrange(p1, p2, p3, p4,p5,p6,p7,p8,p9,p10,p11,p12, nrow = 3)



```


# age 
## age only

```{r}
# all ages (days)

ma_data %>% 
ggplot(aes(x = mean_age, y = d_calc, size = n_1)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days)") +
  theme_classic() +
  theme(legend.position = "none") 

# all ages (months)

ggplot(ma_data, aes(x = (mean_age/30.44), 
                                 y = d_calc, 
                                 size = n_1)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months)") +
  theme_classic() +
  theme(legend.position = "none")

# Younger than 50 months 

ma_data %>% filter(mean_age <= 50*30.44) %>% 
  ggplot( mapping = aes(x = mean_age, y = d_calc, size = n_1)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), younger than 50 months") +
  theme_classic() +
  theme(legend.position = "none")

ma_data %>% filter(mean_age <= 50*30.44) %>% 
  ggplot(mapping = aes(x = mean_age/30.44, y = d_calc, size = n_1)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), younger than 50 months") +
  theme_classic() +
  theme(legend.position = "none")

# younger than 36 months
  
ma_data %>% filter(mean_age <= 36*30.44) %>% 
  ggplot(mapping = aes(x = mean_age, y = d_calc, size = n_1)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), younger than 36 months") +
  theme_classic() +
  theme(legend.position = "none")

ma_data %>% filter(mean_age <= 36*30.44) %>% 
  ggplot(mapping = aes(x = mean_age/30.44, y = d_calc, size = n_1)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), younger than 36 months") +
  theme_classic() +
  theme(legend.position = "none")



```
## age and sentence structure 
```{r}

ma_data_no_bare_verb <- ma_data %>% filter(sentence_structure != "bare_verb")

# all ages (days)
ggplot(data = ma_data_no_bare_verb, aes(x = mean_age, y = d_calc, color = sentence_structure)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days)") +
  theme_classic() 

# all ages (months)

ggplot(data = ma_data_no_bare_verb, aes(x = (mean_age/30.44), y = d_calc, color = sentence_structure)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days)") +
  theme_classic() 

# Younger than 50 months 
ma_data_no_bare_verb_less_50 <- ma_data_no_bare_verb %>% filter(mean_age < 50*30.44 |mean_age==50*30.44)

ggplot(data = ma_data_no_bare_verb_less_50, mapping = aes(x = mean_age, y = d_calc, color = sentence_structure)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), younger than 50 months") +
  theme_classic() 

ggplot(data = ma_data_no_bare_verb_less_50, mapping = aes(x = mean_age/30.44, y = d_calc, color = sentence_structure)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), younger than 50 months") +
  theme_classic() 

# younger than 36 months

ma_data_no_bare_verb_less_36 <- ma_data_no_bare_verb %>% filter(mean_age < 36*30.44|mean_age  == 36*30.44)

ggplot(data = ma_data_no_bare_verb_less_36, mapping = aes(x = mean_age, y = d_calc, color = sentence_structure)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days), younger than 36 months") +
  theme_classic() 

ggplot(data=ma_data_no_bare_verb_less_36, mapping = aes(x = mean_age/30.44, y = d_calc, color = sentence_structure)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("Age (months)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (months), younger than 36 months") +
  theme_classic() 
```

## age and others

```{r}
ma_data %>% 
ggplot(aes(x = mean_age, y = d_calc, color = population_type)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days) break down by population type") +
  theme_classic() -> ae1


ma_data %>% 
ggplot(aes(x = mean_age, y = d_calc, color = stimuli_modality)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days) break down by stimuli_modality") +
  theme_classic() -> ae2

ma_data %>% 
ggplot(aes(x = mean_age, y = d_calc, color = stimuli_actor)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days) break down by stimuli_actor") +
  theme_classic() -> ae3

ma_data %>% 
ggplot(aes(x = mean_age, y = d_calc, color = character_identification)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days) break down by character_identification") +
  theme_classic() -> ae4

ma_data %>% 
ggplot(aes(x = mean_age, y = d_calc, color = practice_phase)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days) break down by practice phase") +
  theme_classic() -> ae5

ma_data %>% 
ggplot(aes(x = mean_age, y = d_calc, color = test_mass_or_distributed)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days) break down by test type") +
  theme_classic() -> ae6

ma_data %>% 
ggplot(aes(x = mean_age, y = d_calc, color = presentation_type)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days) break down by presentation type") +
  theme_classic() -> ae7

ma_data %>% 
ggplot(aes(x = mean_age, y = d_calc, color = test_type)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("Age (days)") +
  ggtitle("Syntactical Bootstrapping effect size vs. Age (days) break down by test type") +
  theme_classic() -> ae8

grid.arrange(ae1,ae2,ae3,ae4, nrow = 2)
grid.arrange(ae5,ae6,ae7, ae8, nrow =2)
ae1
ae2
ae3
ae4
ae5
ae6
ae7
ae8
```



## Models
```{r}
m1 <- rma.mv(d_calc, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m1)
```

### Age
```{r}
m2 <- rma.mv(d_calc ~ mean_age , V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m2)
```

### Age + sentence structure 
```{r}
m3 <- rma.mv(d_calc ~ mean_age + sentence_structure , V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_no_bare_verb)
summary(m3)
```
### Age + sentence structure & interaction??
```{r}
m4 <- rma.mv(d_calc ~ mean_age + sentence_structure + mean_age*sentence_structure , V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_no_bare_verb)
summary(m4)
```
#vocab

productive_vocab_median has more entries than productive_vocab_mean, so using productive_vocab_median here
```{r}
ma_data %>% 
  filter(productive_vocab_median != "NA") %>% 
  mutate(productive_vocab_median = as.numeric(productive_vocab_median))-> ma_data_vocab_median 
 
```

#vocab
## vocab and age 
```{r}
ma_data_vocab_median %>% 
  ggplot(aes(x = productive_vocab_median, y = mean_age)) +
  geom_point() + 
  geom_smooth(method = "lm") + 
  labs(title = "median productive vocabulary and age by day")

```

## vocab and effect size
```{r}
ma_data_vocab_median %>% 
  ggplot(aes(x = productive_vocab_median, y = d_calc)) +
  geom_point() + 
  geom_smooth(method = "lm") + 
  labs(title = "median productive vocabulary and sample size")


```

## model:
```{r}
m4 <- rma.mv(d_calc ~ productive_vocab_median  , V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data_vocab_median)
summary(m4)
```


# n_repetition sentence
## age and n_repetition
older kiddos have less repetitions
```{r}
ma_data %>% 
  ggplot(mapping = aes(x = mean_age, y = n_repetitions_sentence)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("number of repetition per novel verb") +
  xlab("mean_age") +
  ggtitle("mean_age vs. number of repetitions for verb (all)") +
  theme_classic() +
  theme(legend.position = "none")

ma_data %>% filter(mean_age <= 50*30.44) %>% 
  ggplot( mapping = aes(x = mean_age, y = n_repetitions_sentence)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("number of repetition per novel verb") +
  xlab("mean_age") +
  ggtitle("mean_age vs. number of repetitions for verb (all), younger than 50 months") +
  theme_classic() +
  theme(legend.position = "none")

ma_data %>% filter(mean_age <= 36*30.44) %>% 
  ggplot( mapping = aes(x = mean_age,y = n_repetitions_sentence)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("number of repetition per novel verb") +
  xlab("mean_age") +
  ggtitle("mean_age vs. number of repetitions for verb (all), younger than 36 months") +
  theme_classic() +
  theme(legend.position = "none")
```


does not seem to correlate with effect sizes
```{r}
ma_data %>% 
  ggplot(mapping = aes(x = n_repetitions_sentence, y = d_calc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylab("Effect Size") +
  xlab("number of repetition per novel verb") +
  ggtitle("Syntactical Bootstrapping effect size vs. number of repetitions for verb") +
  theme_classic() +
  theme(legend.position = "none")

ma_data %>% 
  ggplot(mapping = aes(x = n_repetitions_sentence, y = d_calc, color = test_mass_or_distributed)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("number of repetition per novel verb") +
  ggtitle("Syntactical Bootstrapping effect size vs. number of repetitions for verb") +
  theme_classic() 

ma_data %>% 
  ggplot(mapping = aes(x = n_repetitions_sentence, y = d_calc, color = character_identification)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("number of repetition per novel verb") +
  ggtitle("Syntactical Bootstrapping effect size vs. number of repetitions for verb (break down by character identification)") +
  theme_classic() 

ma_data %>% 
  ggplot(mapping = aes(x = n_repetitions_sentence, y = d_calc, color = practice_phase)) +
  geom_point() +
  ylab("Effect Size") +
  xlab("number of repetition per novel verb") +
  ggtitle("Syntactical Bootstrapping effect size vs. number of repetitions for verb (break down by practice phase)") +
  theme_classic() 
```

## model  
```{r}
m5 <- rma.mv(d_calc ~ n_repetitions_sentence , V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m5)

m6 <- rma.mv(d_calc ~ n_repetitions_sentence + mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m6)

m7 <- rma.mv(d_calc ~ n_repetitions_sentence + mean_age + n_repetitions_sentence * mean_age, V = d_var_calc,
                            random = ~ 1 | short_cite, data = ma_data)
summary(m7)
```


# argument types 

```{r}
ma_data 


cis_by_at <- ma_data %>%
    group_by(agent_argument_type) %>%
    summarize(mean = mean(d_calc),
            sd = sd(d_calc),
            n = n()) %>%
    mutate(ci_range_95 =  1.96 * (sd/sqrt(n)),
         ci_lower = mean - ci_range_95,
         ci_upper = mean + ci_range_95)

ma_data %>% filter(agent_argument_type == "pronoun" | agent_argument_type == "noun") -> ma_data_by_at
cis_by_at %>% filter(agent_argument_type == "pronoun" | agent_argument_type == "noun") -> cis_by_at

ggplot(data=ma_data_by_at, aes(x = agent_argument_type, 
                    y = d_calc, 
                    color = agent_argument_type)) +
  geom_violin() +
  geom_point(alpha = .4)  +
  ylab("Effect Size") +
  xlab("Agent Argument Type") +
  ggtitle("SB effect size by agent argument type") +
  geom_errorbar(data = cis_by_at, 
                  aes(x = agent_argument_type,
                      y = mean, ymin = ci_lower, 
                      ymax = ci_upper), 
                  color = "black") +
  geom_pointrange(data = cis_by_at, 
                  aes(x = agent_argument_type,
                      y = mean, ymin = ci_lower, 
                      ymax = ci_upper), 
                  color = "black") +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  theme_classic(base_size = 16) +
  theme(legend.position = "none")

ggplot(data=ma_data_by_at, aes(x = agent_argument_type, 
                    y = d_calc, 
                    color = agent_argument_type)) +
  geom_violin() +
  geom_point(alpha = .4)  +
  ylab("Effect Size") +
  xlab("Agent Argument Type") +
  ggtitle("SB effect size by agent argument type") +
  geom_errorbar(data = cis_by_at, 
                  aes(x = agent_argument_type,
                      y = mean, ymin = ci_lower, 
                      ymax = ci_upper), 
                  color = "black") +
  geom_pointrange(data = cis_by_at, 
                  aes(x = agent_argument_type,
                      y = mean, ymin = ci_lower, 
                      ymax = ci_upper), 
                  color = "black") +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  facet_wrap(~sentence_structure) + 
  theme_classic(base_size = 16) +
  theme(legend.position = "none") 


ma_data_by_at %>% 
  filter(sentence_structure == "transitive") %>% 
  filter(patient_argument_type == "pronoun" | patient_argument_type == "noun") -> ma_data_by_pat
  
cis_by_pat <- ma_data_by_pat %>%
    group_by(patient_argument_type) %>%
    summarize(mean = mean(d_calc),
            sd = sd(d_calc),
            n = n()) %>%
    mutate(ci_range_95 =  1.96 * (sd/sqrt(n)),
         ci_lower = mean - ci_range_95,
         ci_upper = mean + ci_range_95)

ggplot(data=ma_data_by_pat, aes(x = patient_argument_type, 
                    y = d_calc, 
                    color = patient_argument_type)) +
  geom_violin() +
  geom_point(alpha = .4)  +
  ylab("Effect Size") +
  xlab("Patient Argument Type") +
  ggtitle("SB effect size by patient argument type") +
  geom_errorbar(data = cis_by_pat, 
                  aes(x = patient_argument_type,
                      y = mean, ymin = ci_lower, 
                      ymax = ci_upper), 
                  color = "black") +
  geom_pointrange(data = cis_by_pat, 
                  aes(x = patient_argument_type,
                      y = mean, ymin = ci_lower, 
                      ymax = ci_upper), 
                  color = "black") +
  facet_wrap(~agent_argument_type) +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  theme_classic(base_size = 16) +
  theme(legend.position = "none") 
   

```


# summary 
## tree plot 

```{r fig.height = 10, fig.width = 5}
ma_model <- rma(ma_data$d_calc, ma_data$d_var_calc)
ma_model
forest(ma_model,
       header = T,
       slab = ma_data$unique_id,
       col = "red",
       cex = .7)
```


## Funnel plot
```{r}
ma_data %>% 
  mutate(color = ifelse(sentence_structure == "transitive", "red", "blue"),
         color_sample_size = ifelse(n_1 < 10, "red", ifelse(n_1 < 20, "orange", "yellow")),
         color_confidence = ifelse(inclusion_certainty == 1, "red", "black"))-> ma_data_funnel

ma_data_funnel %>% filter (abs(d_calc) < 5) -> ma_data_funnel_no_outlier
ss_colors <- ma_data_funnel$color
ss_colors_no_outlier <- ma_data_funnel_no_outlier$color 
size_colors <- ma_data_funnel$color_sample_size
size_colors_no_outlier <- ma_data_funnel_no_outlier$color_sample_size
c_colors <- ma_data_funnel$color_confidence
c_colors_no_outlier <- ma_data_funnel_no_outlier$color_confidence

ma_model_funnel <- rma(ma_data_funnel$d_calc, ma_data_funnel$d_var_calc)
ma_model_funnel_no_outlier <- rma(ma_data_funnel_no_outlier$d_calc, ma_data_funnel_no_outlier$d_var_calc)

f1<- funnel(ma_model_funnel, xlab = "Effect Size", col = ss_colors) 
legend("topright",bg = "white",legend = c("transitive","intransitive"),pch=16,col=c("red", "blue"))
title(main = "All effect sizes break down by sentence structure")

f2<- funnel(ma_model_funnel_no_outlier, xlab = "Effect Size", col = ss_colors_no_outlier) 
legend("topright",bg = "white",legend = c("transitive","intransitive"),pch=16,col=c("red", "blue"))
title(main = "effect sizes excluded outliers (abs <5) break down by sentence structure")

f3<- funnel(ma_model_funnel, xlab = "Effect Size", col = size_colors) 
legend("topright",bg = "white",legend = c("small(<10)","medium(10-20)", "large(>20)"),pch=16,col=c("red", "orange", "yellow"))
title(main = "all effect sizes break down by sample size")

f4<- funnel(ma_model_funnel_no_outlier, xlab = "Effect Size", col = size_colors_no_outlier) 
legend("topright",bg = "white",legend = c("small(<10)","medium(10-20)", "large(>20)"),pch=16,col=c("red", "orange", "yellow"))
title(main = "effect sizes excluded outliers (abs <5) break down by sample size")


f5<- funnel(ma_model_funnel, xlab = "Effect Size", col = c_colors) 
legend("topright",bg = "white",legend = c("weird ones","normal ones"),pch=16,col=c("red", "black"))
title(main = "all effect sizes break down by confidence")

f6<- funnel(ma_model_funnel_no_outlier, xlab = "Effect Size", col = c_colors_no_outlier) 
legend("topright",bg = "white",legend = c("weird ones","normal ones"),pch=16,col=c("red", "black"))
title(main = "effect sizes excluded outliers (abs <5) break down by confidence")


```
