---
title: "Nested vs. Unnested mixed effect models"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc_float: yes
    code_folding: hide 
    number_sections: no
    toc: yes
---


```{r setup, include = F}
library(tidyverse)
library(metafor)
library(knitr)
library(here) # here package manages paths in a sane way
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.height=6, fig.path='Figs/',
                     warning=FALSE, message=FALSE)
theme_set(theme_classic()) # sets global plot theme
```


```{r}
DATA_PATH <- here("data/processed/syntactic_bootstrapping_tidy_data.csv") 

ma_data <- read_csv(DATA_PATH) %>% 
  filter(paradigm_type == "action_matching") %>%
  select(3,6,9, 11:16:61) %>%
  mutate(row_id = 1:n())

ma_data_no_naigles <- ma_data %>%
  filter(same_infant != "naigles2011")

```

Here's what the data look like:
```{r}
DT::datatable(ma_data_no_naigles)
```


Here are models with random effects by study (`unique_id`) and effect size (`row_id`). They give prett

```{r}
rma.mv(d_calc, V = d_var_calc,
                      random = ~ 1 | unique_id,
                      method = "REML",
                      data = ma_data_no_naigles)

rma.mv(d_calc, V = d_var_calc,
                      random = ~ 1 | unique_id/row_id,
                      method = "REML",
                      data = ma_data_no_naigles)
```

This is a consequential decision because it affects one of our key moderators: 

```{r}
rma.mv(d_calc ~ sentence_structure, V = d_var_calc,
                      random = ~ 1 | unique_id,
                      method = "REML",
                      data = ma_data_no_naigles)

rma.mv(d_calc~ sentence_structure + mean_age, V = d_var_calc,
                      random = ~ 1 | unique_id/same_infant/row_id,
                      method = "REML",
                      data = ma_data_no_naigles)

rma.mv(d_calc~ sentence_structure, V = d_var_calc,
                      random = ~ 1 | unique_id/same_infant,
                      method = "REML",
                      data = ma_data_no_naigles)
```



```{r}
rma.mv(d_calc ~ sentence_structure, V = d_var_calc,
                      random = ~ 1 | unique_id,
                      method = "REML",
                      data = ma_data)

rma.mv(d_calc~ sentence_structure, V = d_var_calc,
                      random = ~ 1 | unique_id/same_infant/row_id,
                      method = "REML",
                      data = ma_data)

rma.mv(d_calc~ sentence_structure, V = d_var_calc,
                      random = ~ 1 | unique_id/same_infant,
                      method = "REML",
                      data = ma_data)
``

